---
title: "elephants-3-pilot"
author: "MH Tessler"
date: "1/17/2019"
output: github_document
---

[Link to experiment](http://www.mit.edu/~tessler/projects/elephants/experiments/elephants-3.html)

### Changes from Pilot 2

- ask about both properties
- enrich chapter to provide more context for the mutual exclusivity
- add items
- change "ticks carry lyme disease" to get "cats get cancer", add "lions lay eggs"
- memory check to test actually tested properties

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(ggpirate)
library(brms)
library(jsonlite)
theme_set(theme_few())
data.path <- "../../data/elephants-3/elephants-3"
```

## Subject Information

```{r}
df.subj <- read_csv(
  paste(data.path, "-subject_information.csv", sep = "")
  ) %>%
  mutate(language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))

df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks 

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- birds are male (coded as correct if 0.25 < x < 0.75)
- cats get cancer (coded as correct if x < 0.75) [being generous with this one]
- lions lay eggs (coded as correct if x < 0.10)

```{r}
df.attn <- read_csv(
  paste(data.path, "-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition))

# slider bar check

df.slider_check <- df.attn %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 & response < 0.75,
    property == "cats get cancer" ~ response < 0.5,
    property == "lions lay eggs" ~ response < 0.1
  )) 

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>% 
  summarize(not_all_correct = sum(correct) < 4,
            not_three_correct = sum(correct) < 3,
            n_correct = sum(correct))

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

df.slider_check %>% 
  group_by(property) %>%
  summarize(sum(correct)) %>%
  kable()

df.slider_check %>% 
  group_by(workerid) %>%
  summarize(n_correct = sum(correct)) %>%
  group_by(n_correct) %>% count() %>%
  kable()
```

### Memory check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.

```{r}
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")
```

### Slider Practice and Memory Check

```{r}
df.mmry %>%
  select(workerid, n_correct) %>%
  left_join(df.slider_check.workers %>% select(workerid, n_correct), by=c("workerid")) %>%
  rename(n_correct_memory = n_correct.x, n_correct_slider = n_correct.y) %>%
  ggplot() +
  geom_count(aes(x = n_correct_memory, y = n_correct_slider))
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1) 

df.expln %>%
  select(workerid, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

## Participants

```{r}
df.trials <- left_join(
    read_csv(
    paste(data.path, "-trials.csv", sep = "")
    ) %>% 
    mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      quantifier = gsub("\"", "", quantifier),
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders
      ),
    df.mmry %>% select(workerid, n_correct)
)

df.query <- df.trials %>%
  filter(page_type == "query") %>%
  gather(key, val, response_1, response_2)
```

### Included/Excluded Subject Numbers
Removing participants who got fewer than 7 correct on memory check and didn't get all 4 sliders. (Participants with bad explanations usually fell into one of these other groups.)

```{r}
df.query %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln) %>%
  group_by(memory_fail, slider_fail) %>% count() %>% kable()
```

### Prevalence Estimates by Participant
 
Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.
* fill = number of correct responses on the memory check (out of 10)
* facet = participants

```{r}
df.query  %>%
  ggplot(., aes( x = val, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## Filler Trials

These used quantifiers (and thus we have strong idea about literal meaning).

```{r}
df.query.filler <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num, rt, trial_type, quantifier, page_type, key, val)

df.query.filler  %>%
  ggplot(., aes( x = val ))+
  geom_histogram(aes(y = ..density.. *0.05, binwidth = 0.05))+
  ylab("Proportion") +
  facet_wrap(~quantifier + condition)
```

## Critical Trials (collapsed across item)

```{r}
df.query.critical <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, predicate_2, key, val, page_type, memory_fail, slider_fail) %>%
  filter(trial_type == "critical") %>%  
  mutate(condition = factor(condition, levels = c("uninterrupted_irrelevant", "uninterrupted"),
                            labels = c('"..live in Africa and eat bugs"', 
                                       '"..live in Africa and Asia"')),
         key = factor(key, levels = c("response_1", "response_2"),
                      labels = c("% live in Africa", "% live in Asia")))

df.query.critical %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(key~condition)
```

### Mutual Exclusivity

```{r}
df.query.critical %>%
  spread(key, val) %>%
  mutate(mutually_exclusive = `% live in Africa` + `% live in Asia` <= 1.00) %>%
  group_by(condition, mutually_exclusive) %>%
  count() %>%
  ggplot(aes(x = condition, y = n)) +
  geom_col(aes(fill = mutually_exclusive))
```


### Bootstrapped 95% Confidence Intervals (collapsed across item)

```{r}
df.bs.query.critical <- df.query.critical %>%
  group_by(condition, key) %>%
  tidyboot_mean(column = val)
```

```{r}
df.bs.query.critical %>%
  ggplot(., aes( x = condition, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(data = df.query.critical, position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = key), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 15, vjust = 0.5, hjust = 0.5))

#ggsave(paste(fig.path, "expt1_summary.pdf", sep = ""), height = 3.8, width = 5.5)
```

```{r}
df.query.critical %>%
  ggplot(., aes( x = condition, y = val))+
  geom_pirate(aes(color = key, fill = key),
              violins = F, show.legend = TRUE)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = , vjust = 1, hjust = 1))
```

## Modeling

```{r eval = F, cache = TRUE}
rs.brm <- brm(data = df.query.critical,
    formula = val ~ key * condition + 
      (1 + key*condition | workerid) +
      (1 + key*condition | predicate_1),
    family = "zero_one_inflated_beta",
    iter = 2000, warmup = 1000, thin = 1,
    chains = 2, cores = 2)

rs.brm.simple <- brm(data = df.query.critical %>%
                filter(key == "% live in Africa"),
    formula = val ~ condition + 
      (1 + condition | workerid) +
      (1 + condition | predicate_1),
    family = "zero_one_inflated_beta",
    iter = 2000, warmup = 1000, thin = 1,
    chains = 3, cores = 3)

summary(rs.brm.simple)
```

## By-item Analyses

### Items
Items can be categorized by the continuation type and the coordination type.  

* continuation type: the interrupted sentence containing the questioned properties varies according to how real the subject matter is.  
    + real: Sentence and properties are completely real.  
    + fakeNames: The properties concern real items (like religion), but the name is made-up (Daith).  
    + fakeDefs: The properties concern completely made-up items.  
* coordination type: the "and" conjoins different syntactic categories  

```{r}
items <- fromJSON("../cogsci2019/items-1.json")
items %>%
  group_by(coordination, continuationType) %>%
  count() %>%
  kable()
```

### Number of Responses by Item and Condition

```{r}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ungroup() %>%
  group_by(condition, predicate_1, predicate_2) %>%
  count() %>%
  spread(condition, n) %>% 
  left_join(select(items, property1, property2, continuationType, coordination), by = c("predicate_1" = "property1", "predicate_2" = "property2")) %>%
  replace(is.na(.), 0) %>% # missing combinations of condition and predicate means no trials were collected
  kable()
```

### Pirate Plots (by item)

```{r fig.width=14, fig.height=7}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F, show.legend = TRUE)+
  facet_wrap(~predicate_1+predicate_2, nrow = 2)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### Pirate Plots (by Coordination)

```{r fig.width=14, fig.height=7}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  left_join(select(items, property1, property2, continuationType, coordination), by = c("predicate_1" = "property1", "predicate_2" = "property2")) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F, show.legend = TRUE)+
  facet_wrap(~coordination)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### Pirate Plots (by Realness)

```{r fig.width=14, fig.height=7}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  left_join(select(items, property1, property2, continuationType, coordination), by = c("predicate_1" = "property1", "predicate_2" = "property2")) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F, show.legend = TRUE)+
  facet_wrap(~continuationType)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## First Trial

```{r}
df.query.critical %>%
  group_by(workerid, condition, key) %>%
  mutate(first_trial  = min(chapter_num),
         is_first = chapter_num == first_trial) %>%
  filter(is_first) %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(condition~key)+
  xlim(0, 1)
```

## Reaction Times

*how much time do participants spend on the question slide?*

### Density Graph of Reaction Times by Condition

```{r}
df.query.critical %>%
  filter(key == "% live in Africa") %>%
  ggplot(., aes( x = log(rt / 1000) , color = condition, fill = condition))+
  geom_density(aes(y = ..density..), alpha = 0.3)+
  xlab("log time in seconds")
```

### Modeling of Response Times

```{r}
brm.rt <-  brm(
    data = df.query.critical %>%
            filter(key == "% live in Africa") %>%
            mutate(logrt = log(rt / 1000)), 
    logrt ~ condition,
    iter = 2000, warmup = 1000, thin = 1,
    chains = 3, cores = 3)
  
summary(brm.rt)
```