---
title: "elephants-7-single"
output: html_document
---

## Experiment 2 for CogSci 2019 (Elephants-7), with a single question (Africa only)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(jsonlite)
library(gridExtra)
library(lme4)
library(brms)
library(bayesplot)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(broom)
library(tidybayes)
library(modelr)
library(ggridges)
library(ggstance)
theme_set(theme_few())
data.path <-"../../data/elephants-7-single/"
```

##
```{r}
result.files <- list.files(data.path, pattern="json")
  df.subj <- data.frame()
  df.trials <- data.frame()
  df.attn <- data.frame()
  for (result_file in result.files) {

    result_json = fromJSON(paste(data.path, result_file, sep ="/"))
    worker.id = result_json$WorkerId
    condition = result_json$answers$condition

    df.attn = bind_rows(
      df.attn,
      data.frame(result_json$answers$catch_trials) %>%
        mutate(workerid = worker.id)
    )

    df.subj = bind_rows(
      df.subj,
      data.frame(result_json$answers$subject_information) %>%
        mutate(workerid = worker.id,
               language = gsub("\"", "", language),
           enjoyment = gsub("\"", "", enjoyment),
           age = gsub("\"", "", age),
           gender = gsub("\"", "", gender),
           problems = gsub("\"", "", problems),
           comments = gsub("\"", "", comments))
    )

    df.trials = bind_rows(
      df.trials,
      data.frame(result_json$answers$trials) %>%
        mutate(workerid = worker.id, condition = condition)
    )
  }
```


## Subject Information

```{r}
df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- cats get cancer (coded as correct if x < 0.75) [being generous with this one]
- lions lay eggs (coded as correct if x < 0.10)

```{r}
# slider bar check

df.slider_check <- df.attn %>%
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  ))

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>%
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 3,
    )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

# number of participants grouped by number of correct sliders
df.slider_check %>%
  group_by(workerid) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

# number of correct responses grouped by slider question
df.slider_check %>%
  group_by(property) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.
```{r}
# memory check data
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`,
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits)

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")
```

### Slider Practice and Memory Check

```{r}
df.mmry %>%
  select(workerid, n_correct) %>%
  left_join(df.slider_check.workers %>% select(workerid, n_correct), by=c("workerid")) %>%
  rename(n_correct_memory = n_correct.x, n_correct_slider = n_correct.y) %>%
  ggplot() +
  geom_count(aes(x = n_correct_memory, y = n_correct_slider))
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1 | is.na(correct)) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

### Exclusions

```{r}
workers.to.exclude <- unique(c(workers.fail.memory, workers.fail.sliders))
```

## Participants

```{r}
df.trials <- left_join(
  df.trials %>%
    mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders,
    ),
  df.mmry %>% select(workerid, n_correct))

df.query <- df.trials %>%
  filter(page_type == "query") %>%
   mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders,
    ) %>%
  gather(key, val, response_1)
```

### Included/Excluded Subject Numbers

Removing participants who got fewer than 7 correct on memory check and didn't get all 3 sliders. (Participants with bad explanations usually fell into one of these other groups.)

```{r}
df.query %>%
  distinct(workerid, memory_fail, slider_fail) %>%
  group_by(memory_fail, slider_fail) %>% count() %>% kable()
```

## Critical Trials (collapsed across item)

```{r}
df.query.critical <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, 
         key, val, page_type, memory_fail, slider_fail) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(condition = ifelse(condition %in% c("before", "after"),
                            "AF&AS_unint", condition),
    condition = factor(condition, 
                            levels = c("int1", 
                                       "int2",
                                       "int4",
                                       "AF&AS_unint"),
                            labels = c('"...live in Africa" [?]',
                            '"... and" [?]',
                                       '"... Asia" [?]',
                                       '"...Africa and Asia." [?]')
  ))
```

```{r}
data.path.orig <- "../../data/elephants-7-full/elephants-7-full"

df.attn.orig <- read_csv(
  paste(data.path.orig, "-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition),
         workerid = as.character(workerid))

df.slider_check.orig <- df.attn.orig %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  ),
  workerid = as.character(workerid)) 

df.slider_check.workers.orig <- df.slider_check.orig %>%
  group_by(workerid) %>% 
  summarize(
    n_correct = sum(correct, na.rm = TRUE),
    not_all_correct = n_correct < 3,
    )

workers.fail.sliders.orig <- df.slider_check.workers.orig %>%
  filter(not_all_correct) %>%
  pull(workerid)

df.mmry.orig <- df.attn.orig %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct),
         workerid = as.character(workerid)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory.orig <- df.mmry.orig %>% filter(n_correct < 7) %>% pull(workerid)

df.expln.orig <- df.attn.orig %>%
  filter(correct == -1) %>%
  left_join(., df.mmry.orig %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers.orig %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

df.trials.orig <- left_join(
    read_csv(
    paste(data.path.orig, "-trials.csv", sep = "")
    ) %>% 
    mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      quantifier = gsub("\"", "", quantifier),
      memory_fail = workerid %in% workers.fail.memory.orig,
      slider_fail = workerid %in% workers.fail.sliders.orig,
      workerid = as.character(workerid)
      ),
    df.mmry.orig %>% select(workerid, n_correct)
)

df.query.orig <- df.trials.orig %>%
  filter(page_type == "query") %>%
  gather(key, val, response_1, response_2)

df.query.critical.orig <- df.query.orig %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, predicate_2, 
         key, val, page_type, memory_fail, slider_fail) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(condition = ifelse(condition %in% c("before", "after"),
                            "AF&AS_unint", condition),
    condition = factor(condition, 
                            levels = c("int1", 
                                       "int2",
                                       "int4",
                                       "AF&AS_unint"),
                            labels = c('"...live in Africa" [?]',
                            '"... and" [?]',
                                       '"... Asia" [?]',
                                       '"...Africa and Asia." [?]')
  ),
         key = factor(key, levels = c("response_1", "response_2"),
                      labels = c("% live in Africa", "% live in other place"))) %>%
  mutate(question_type = "both")

df.bs.query.critical.orig <- df.query.critical.orig %>%
  group_by(condition, key) %>%
  tidyboot_mean(column = val)
```

```{r}
df.query.critical.full <- full_join(df.query.critical %>%
                                      mutate(question_type = "single"), df.query.critical.orig %>%
                                      select(-predicate_2) %>%
                                      filter(key == "% live in Africa") %>%
                                      mutate(question_type = "both")) %>% mutate(
  question_type = ifelse(question_type == 'both', 'Both Questions', 'Single Question')
)

df.bs.query.critical <- df.query.critical.full %>%
  group_by(condition, question_type) %>%
  tidyboot_mean(column = val) %>%
  ungroup()

ggplot(df.bs.query.critical, aes( x = condition, fill = question_type))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5, color = 'black')+

  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8,
           alpha = 0.3,
           color = 'black')+
  geom_point(data = df.query.critical.full, 
             position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = question_type),
             alpha = 0.3)+
    geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(0.8), width = 0.3, size = 1.2,
                color = 'black')+  
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"), color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 20, vjust = 0.55, hjust = 0.5),
        legend.position = "right") +
  ggtitle("Experiment 2")

ggsave('rep_data2.png', width=5, height = 3)
```

### Ridge Plots

```{r}
df.query.critical.full.3cond <- df.query.critical.full %>%
         filter(condition != '"...Africa and Asia." [?]') %>%
         mutate(condition=fct_rev(droplevels(condition)))
df.query.critical.full.3cond$condition <- ordered(df.query.critical.full.3cond$condition, c('"... Asia" [?]','"... and" [?]', '"...live in Africa" [?]'))

df.bs.query.critical.3cond <- df.bs.query.critical %>%
                    filter(condition != '"...Africa and Asia." [?]') %>%
         mutate(condition=fct_rev(droplevels(condition)))
df.bs.query.critical.3cond$condition <- ordered(df.bs.query.critical.3cond$condition, c('"... Asia" [?]','"... and" [?]', '"...live in Africa" [?]'))

ggplot(df.query.critical.full.3cond, 
       aes(x = val, y = condition, fill = ..x..)) +
  facet_wrap(~question_type) +
  geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = position_points_jitter(width = 0.01, height = 0),
    point_shape = '|', point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = 'binline', bins = 25, draw_baseline = F
  ) +
  geom_linerangeh(data = df.bs.query.critical.3cond,
    inherit.aes = F,
    aes(xmin = ci_lower, xmax = ci_upper, 
        y = as.numeric(condition)+0.4),
    size = 1.25, color = 'black')+
  geom_point(data = df.bs.query.critical.3cond,
    inherit.aes = F,
    aes(x = mean,
        y = as.numeric(condition)+0.4),
    size = 3, color = 'black', shape = 3)+
  scale_x_continuous(expand = c(0.01, 0), 
                     limits = c(0, 1.03), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_fill_viridis(name = "Implied Prevalence", option = "D",
                     breaks = c(0, 1)) +
  guides(fill = F)+
  #labs(title = 'Temperatures in Lincoln NE in 2016') +
  #theme_ridges(font_size = 13, grid = T) + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(hjust = 0.5, vjust = 0))+
  labs(x = "Implied Prevalence about First Predicate") +
  ggtitle('Experiment 2')

ggsave('~/Desktop/expt2_ridges.png', width=10, height=4)
```

```{r}
and.pred <- read_csv('~/and.csv')

ggplot(df.query.critical.full.3cond %>% 
         filter(question_type == 'Both Questions', condition == '"... and" [?]'),
       aes(x=val)) +
  geom_histogram(aes(y=..count../sum(..count..)), fill=rainbow(30))+
  geom_line(data=Africa.pred, mapping=aes(x=x,y=y)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(hjust = 0.5, vjust = 0))+
  labs(x = "Implied Prevalence about First Predicate") +
  ggtitle('Elephants live in Africa and...')

ggsave('~/Desktop/andOverlay.png', width=7,height=2)
```


### Bootstrapped 95% Confidence Intervals (collapsed across item)

_Property 2_ = "% live in Asia" for ME trials and "% eat bugs" for NME trials

```{r}


df.bs.query.critical %>%
  ggplot(., aes( x = condition))+
  theme_black()+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5, color = 'white')+

  geom_point(data = df.query.critical, 
             inherit.aes = F, aes(x = condition, y = val), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.5, color = 'white')+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2, color='white')+  
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(#axis.text.x = element_text(angle = 30, vjust = 0.55, hjust = 0.5),
        legend.position = "top")


```

```{r}
my.backward.diff = matrix(c(-3/4, 1/4, 1/4, 1/4, -1/2, -1/2, 1/2, 1/2, -1/4, -1/4, -1/4, 3/4), ncol = 3) 
df.query.results <- df.query.critical.full %>%
  mutate(
    condition = case_when(
      condition == '"...live in Africa" [?]' ~ "Af",
      condition == '"... and" [?]' ~ "and",
      condition == '"... Asia" [?]' ~ "As",
      condition == '"...Africa and Asia." [?]' ~ "AfandAs"
    )
  )
df.query.results$condition <- factor(df.query.results$condition, levels=c("Af", "and", "As", "AfandAs"), ordered=TRUE)
contrasts(df.query.results$condition) <- my.backward.diff
fit4 <- brm(val ~ condition + (1 + condition | workerid) + (1 + condition | predicate_1), df.query.results %>% filter(question_type == 'Both Questions'))
summary(fit4)
fit5  <- brm(val ~ condition + (1 + condition | workerid) + (1 + condition | predicate_1), df.query.results %>% filter(question_type == 'Single Question'))
summary(fit5)
coef <- tidy(fit4, prob=0.95)
stanplot(fit4)
coef %>% write.csv('model_coef.csv')
```

