---
title: "CogSci Experiment 1 (single question, same screen)"
author: "Karen Gu"
date: "9/6/2019"
output: github_document
---

[Link to experiment](https://www.mit.edu/~karengu/elephants_expt1_single_samescreen/elephants/experiments/elephants-11.html)

## elephants-3, single question, same screen
Experiment 1 for CogSci 2019 (Elephants-3i), with a single question (Africa only), all info presented on the same screen

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(jsonlite)
library(gridExtra)
library(lme4)
library(brms)
library(bayesplot)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(broom)
library(tidybayes)
library(modelr)
library(ggridges)
library(ggstance)
theme_set(theme_few())
data.path <-"../../data/elephants-3-single-samescreen/"
```

##
```{r}
result.files <- list.files(data.path, pattern="json")
  df.subj <- data.frame()
  df.trials <- data.frame()
  df.attn <- data.frame()
  for (result_file in result.files) {

    result_json = fromJSON(paste(data.path, result_file, sep ="/"))
    worker.id = result_json$WorkerId
    condition = result_json$answers$condition

    df.attn = bind_rows(
      df.attn,
      data.frame(result_json$answers$catch_trials) %>%
        mutate(workerid = worker.id)
    )

    df.subj = bind_rows(
      df.subj,
      data.frame(result_json$answers$subject_information) %>%
        mutate(workerid = worker.id,
               language = gsub("\"", "", language),
           enjoyment = gsub("\"", "", enjoyment),
           age = gsub("\"", "", age),
           gender = gsub("\"", "", gender),
           problems = gsub("\"", "", problems),
           comments = gsub("\"", "", comments))
    )

    df.trials = bind_rows(
      df.trials,
      data.frame(result_json$answers$trials) %>%
        mutate(workerid = worker.id, condition = condition)
    )
  }
```


## Subject Information

```{r}
df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- birds are male (coded as correct if 0.25 < x < 0.75)
- cats get cancer (coded as correct if x < 0.75) [being generous with this one]
- lions lay eggs (coded as correct if x < 0.10)

```{r}
# slider bar check

df.slider_check <- df.attn %>%
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 & response < 0.75,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  ))

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>%
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 4,
    not_three_correct = n_correct < 3
    )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

# number of participants grouped by number of correct sliders
df.slider_check %>%
  group_by(workerid) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

# number of correct responses grouped by slider question
df.slider_check %>%
  group_by(property) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.
```{r}
# memory check data
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`,
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits)

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")
```

### Slider Practice and Memory Check

```{r}
df.mmry %>%
  select(workerid, n_correct) %>%
  left_join(df.slider_check.workers %>% select(workerid, n_correct), by=c("workerid")) %>%
  rename(n_correct_memory = n_correct.x, n_correct_slider = n_correct.y) %>%
  ggplot() +
  geom_count(aes(x = n_correct_memory, y = n_correct_slider))
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1 | is.na(correct)) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

### Exclusions

```{r}
workers.to.exclude <- unique(c(workers.fail.memory, workers.fail.sliders))
```

## Participants

```{r}
df.trials <- left_join(
  df.trials %>%
    mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders
    ),
  df.mmry %>% select(workerid, n_correct))

df.query <- df.trials %>%
   mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders
    ) %>%
  gather(key, val, response)
```

### Included/Excluded Subject Numbers

Removing participants who got fewer than 7 correct on memory check and didn't get all 4 sliders. (Participants with bad explanations usually fell into one of these other groups.)

```{r}
df.query %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln) %>%
  group_by(memory_fail, slider_fail) %>% count() %>% kable()
```

### Prevalence Estimates by Participant

Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.
* fill = number of correct responses on the memory check (out of 10)
* facet = participants

```{r}
df.query  %>%
  ggplot(., aes( x = val, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## Filler Trials

These used quantifiers (and thus we have strong idea about literal meaning).

```{r}
df.query.filler <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num,
         rt, trial_type, quantifier, key, val)

df.query.filler  %>%
  ggplot(., aes( x = val ))+
  geom_histogram(aes(y = ..density.. *0.05, binwidth = 0.05))+
  ylab("Proportion") +
  facet_grid(condition~quantifier)
```

## Critical Trials (collapsed across item)

## Histograms of Prevalence Estimates by Condition (collapsed across item)
```{r}
df.query.critical <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt,
         trial_type, predicate_1,
         key, val, memory_fail, slider_fail, chapter) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate( me_status = ifelse(condition %in% c("interrupted", "uninterrupted"),
                             "Mutually Exclusive", "Non Mutually Exclusive"),
          interrupted = ifelse(condition %in% c("interrupted", "nme_interrupted"),
                             '\"...live in Africa\"', '\"...Africa and {Asia / eat bugs}\"'),
          interrupted = factor(interrupted, levels = c( '\"...live in Africa\"', '\"...Africa and {Asia / eat bugs}\"')),
          condition2 = factor(condition,
                  levels = c("interrupted",
                             "uninterrupted",
                             "nme_interrupted",
                             "nme_uninterrupted"),
                  labels = c('"...Africa"',
                             '"...Africa and Asia"',
                             '"...Africa"',
                             '"...Africa and eat bugs"'))) %>%
  mutate(me = if_else(str_detect(condition, "bugs"), "nme", "me"),
         interrupted = if_else(str_detect(condition, "and"), "uninterrupted", "interrupted")) %>%
  mutate(question_type = "single")

df.query.critical %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_wrap(~condition2)
```

```{r}
# data from cogsci experiment 1

df.expt1.attn <- read_csv(
  paste("../../data/elephants-3i/elephants-3i-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition),
         workerid = as.character(workerid),
         correct = case_when(correct == "true" ~ 1,
                             correct == "false" ~ 1,
                             correct == "1" ~ 1,
                             correct == "0" ~ 0))
df.expt1.slider_check <- df.expt1.attn %>%
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 & response < 0.75,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  ))

df.expt1.slider_check.workers <- df.expt1.slider_check %>%
  group_by(workerid) %>%
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 4,
    not_three_correct = n_correct < 3
    )

expt1.workers.fail.sliders <- df.expt1.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)
df.expt1.mmry <- df.expt1.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`,
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits)

expt1.workers.fail.memory <- df.expt1.mmry %>% filter(n_correct < 7) %>% pull(workerid)

expt1.workers.to.exclude <- unique(c(expt1.workers.fail.memory, expt1.workers.fail.sliders))

df.expt1.trials <- read_csv(
    paste("../../data/elephants-3i/elephants-3i-trials.csv", sep = "")
    ) %>% mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      quantifier = gsub("\"", "", quantifier),
      workerid = as.character(workerid)
      ) %>%
    mutate(
      memory_fail = workerid %in% expt1.workers.fail.memory,
      slider_fail = workerid %in% expt1.workers.fail.sliders
    )

df.expt1.query <- df.expt1.trials %>%
  filter(page_type == "query") %>%
   mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders
    ) %>%
  gather(key, val, response_1)

df.expt1.query.critical <- df.expt1.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt,
         trial_type, predicate_1,
         key, val, page_type, memory_fail, slider_fail, chapter) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(question_type = "both")
```

```{r}
# data from single screen replication

df.expt1.single.query.critical <- read.csv('elephants-3-single.csv') %>% 
  select(-X) %>%
  mutate(question_type = "single")
```



### Bootstrapped 95% Confidence Intervals (collapsed across item)

```{r}
df.query.critical.full <- full_join(df.query.critical %>%
                                      mutate(question_type = "samescreen"), df.expt1.single.query.critical) %>% 
  mutate(condition = if_else(condition == 'nme_interrupted', 'interrupted', condition)) %>% 
   full_join(df.expt1.query.critical %>% 
                                      filter(condition != 'nme_interrupted', key=="response_1")
                                    ) %>%
  mutate(condition = factor(condition,
                            levels = c("interrupted",
                                       "uninterrupted",
                                       "nme_uninterrupted"),
                            labels = c('"...live in Africa __"',
                                       '"...and Asia"',
                                       '"...and eat bugs"')),
         question_type = factor(question_type,
                                levels = c("both", "single", "samescreen"),
                                labels = c("Both", "Single", "Same Screen"))) %>%
  select(-me_status, -interrupted, -condition2, -me, -page_type)

df.bs.query.critical <- df.query.critical.full %>%
  group_by(condition, question_type) %>%
  tidyboot_mean(column = val) %>%
  ungroup()

df.bs.query.critical %>%
  ggplot(., aes( x = condition, y = mean, ymin = ci_lower, ymax = ci_upper, fill = question_type ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  xlab("Condition")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  theme(legend.title = element_blank())

ggsave('~/Desktop/expt1_summary.png', width = 10, height = 6)
```

### Pirate Plots (collapsed across item)
```{r}
ggplot(df.bs.query.critical, aes( x = condition, fill = question_type))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5, color = 'black')+

  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8,
           alpha = 0.3,
           color = 'black')+
  geom_point(data = df.query.critical.full, 
             position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = question_type),
             alpha = 0.5)+
    geom_linerange(aes(ymin = ci_lower, ymax = ci_upper),
                position = position_dodge(0.8), width = 0.3, size = 1.2,
                color = 'black')+  
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  #scale_color_manual(values = c("#268bd2", "#859900"))+
  #scale_fill_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"), color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 20, vjust = 0.55, hjust = 0.5),
        legend.position = "right")
```


### Ridge Plots
```{r}
ggplot(df.query.critical.full, 
    aes(x = val, y = condition, fill = ..x..)) +
  facet_grid(~question_type) +
  geom_density_ridges_gradient(
    jittered_points = T, alpha = 0.8, scale = 0.95,
    position = position_points_jitter(width = 0.01, height = 0),
    point_shape = '|', point_size = 2.5, point_alpha = 0.3,
    rel_min_height = 0.01, gradient_lwd = 1,
    stat = 'binline', bins = 25, draw_baseline = F
  ) +
  geom_linerangeh(data = df.bs.query.critical,
  inherit.aes = F,
    aes(xmin = ci_lower, xmax = ci_upper, 
        y = as.numeric(condition)+0.3),
    size = 1.25, color = 'black')+
  geom_point(data = df.bs.query.critical,
    inherit.aes = F,
    aes(x = mean,
        y = as.numeric(condition)+0.3),
    size = 3, color = 'black', shape = 3)+
  scale_x_continuous(expand = c(0.01, 0), 
                     limits = c(0, 1.03), 
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_y_discrete(expand = c(0.01, 0)) +
  scale_fill_viridis(name = "Implied Prevalence about First Predicate", option = "D",
                     breaks = c(0, 1)) +
  guides(fill = F)+
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(hjust = 0.5, vjust = 0))+
  labs(x = "Implied Prevalence about First Predicate") +
  ggtitle('Experiment 1')

```


### Stats

#### Regression
```{r}
model.data <- df.query.critical.full %>% select(workerid, predicate_1, val, condition, question_type)
# dummy coded with "...live in Africa" as base level
fit.expt1 <- brm(val ~ condition + question_type + (1 + condition | workerid) + (1 + condition | predicate_1), model.data)
summary(fit.expt1)
```

