---
title: "elephants-5-pilot"
author: "MH Tessler"
date: "1/28/2019"
output: github_document
---

[Link to experiment](http://www.mit.edu/~tessler/projects/elephants/experiments/elephants-5.html)

## Experiment 5 pilot

All questions interrupting.

- int1: (Africa) -- Q(Af, As) -- (and eat bugs in the wild)
- int2: (Africa and) -- Q(Af, As) -- (eat bugs in the wild)
- int4: (Africa and Asia) -- Q(Af, As) -- (which is warm)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(ggpirate)
theme_set(theme_few())
data.path <- "../../data/elephants-5/elephants-5"
```

## Subject Information

```{r}
df.subj <- read_csv(
  paste(data.path, "-subject_information.csv", sep = "")
  ) %>%
  mutate(language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))

df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks 

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- birds are male (coded as correct if 0.25 < x < 0.75)
- cats get cancer (coded as correct if x < 0.75) [being generous with this one]
- lions lay eggs (coded as correct if x < 0.10)

```{r}
df.attn <- read_csv(
  paste(data.path, "-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition))

df.slider_check <- df.attn %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 & response < 0.75,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  )) 

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>% 
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 4,
    not_three_correct = n_correct < 3
    )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

df.slider_check %>% 
  group_by(workerid) %>%
  summarize(n_correct = sum(correct)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

df.slider_check %>% 
  group_by(property) %>%
  summarize(n_correct = sum(correct)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor).
Note: for this pilot, memory checks were mistakenly asked even though the participant did not see the corresponding chapter. This was resolved for future experiments, beginning at elephants-6.

```{r}
# memory check data
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

bad.expln <- c(11, 19,22, 26)
df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

## Participants

```{r}
df.trials <- left_join(
    read_csv(
    paste(data.path, "-trials.csv", sep = "")
    ) %>% 
    mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      quantifier = gsub("\"", "", quantifier),
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders,
      bad_expln  = workerid %in% bad.expln
      ),
    df.mmry %>% select(workerid, n_correct)
)

df.query <- df.trials %>%
  filter(page_type == "query") %>%
  gather(key, val, response_1, response_2)
```

### Included/Excluded Subject Numbers
Removing participants who got fewer than 7 correct on memory check and didn't get all 4 sliders. (Participants with bad explanations usually fell into one of these other groups.)

```{r}
df.query %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln) %>%
  group_by(memory_fail, slider_fail,bad_expln) %>% count() %>% kable()
```

### Prevalence Estimates by Participant
 
Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.  
* fill = number of correct responses on the memory check (out of 10)  
* facet = participants  

```{r}
df.query  %>%
  ggplot(., aes( x = val, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## Filler Trials

These used quantifiers (and thus we have strong idea about literal meaning).

```{r}
df.query.filler <- df.query %>%
  filter(!slider_fail, !bad_expln) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num, 
         rt, trial_type, quantifier, page_type, key, val)

df.query.filler  %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_wrap(~quantifier + condition)
```

## Critical Trials (collapsed across item)

*Conditions*

1. AF: "Elephants live in Africa" -- Q(Africa, Asia) -- "and breathe oxygen"
2. AF&: "Elephants live in Africa and" -- Q(Africa, Asia) -- "breathe oxygen"
4. AF&AS: "Elephants live in Africa and Asia" -- Q(Africa, Asia) -- "while alive"

### Number of Participants by Condition

```{r}
df.query.critical <- df.query %>%
  filter(!bad_expln, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, predicate_2, 
         key, val, page_type, memory_fail, slider_fail, bad_expln) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(condition = ifelse(condition %in% c("before", "after"),
                            "AF&AS_unint", condition),
    condition = factor(condition, 
                            levels = c("int1", 
                                       "int2",
                                       #"int3",
                                       "int4",
                                       "AF&AS_unint"),
                            labels = c('"...live in Africa __"',
                            '"...live in Africa and __"',
                                       '"...live in Africa and Asia __"',
                                       '"...live in Africa and Asia."')
  ),
         key = factor(key, levels = c("response_1", "response_2"),
                      labels = c("% live in Africa", "% live in Asia")))

df.query.critical %>% 
  filter(key == "% live in Africa") %>%
  group_by(condition) %>% count() %>% kable()
```

### Histograms of Prevalence Estimates by Condition (collapsed across trials)

```{r}
df.query.critical %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(key~condition)
```

### Bootstrapped 95% Confidence Intervals (collapsed across item)

_Property 2_ = "% live in Asia" for ME trials and "% eat bugs" for NME trials

```{r}
df.bs.query.critical <- df.query.critical %>%
  group_by(condition, key) %>%
  tidyboot_mean(column = val)

df.bs.query.critical %>%
  ggplot(., aes( x = condition, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  geom_point(data = df.query.critical, position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = key), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 15, vjust = 0.5, hjust = 0.5))

#ggsave(paste(fig.path, "expt3_summary.pdf", sep = ""), height = 3.4, width = 7)
```

### Pirate Plots (collapsed across item)

```{r}
df.query.critical %>%
  ggplot(., aes( x = condition, y = val))+
  geom_pirate(aes(color = key, fill = key),
              violins = F, show.legend = TRUE)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### Bootstrapped 95% Confidence Intervals for Relationships Between Prevalence Estimates (collapsed across items)

The relationships between prevalence estimates of the mentioned property (property 1) and the other property (property 2) could be:
- mutually exclusive: both properties cannot occur at the same time, so the sum of prevalence estimates cannot exceed 1  
- prevalence for property 1 is greater than property 2  
- property 1 is interpreted as a universal  
- property 2 is interpreted as a universal  
* These conditions are not mutually exclusive; a participant can fall into one or more of the categories for a given trial.

```{r}
df.query.critical %>% spread(key, val) %>% 
  rename(africa = `% live in Africa`,
         asia = `% live in Asia`) %>%
  rowwise() %>%
  mutate(ME = africa + asia < 1.05, # mutually exclusive: both properties cannot exceed 100%
         af_g_as = africa > asia, # prevalence for Africa greater than prevalence for Asia
         universal_af = africa > 0.9, # Africa as universal
         universal_as = asia > 0.9) %>% # Asia as universal
  gather(key, val, ME, af_g_as, universal_af, universal_as) %>%
  group_by(condition, key) %>%
  tidyboot_mean(column = val) %>%
  ggplot(., aes( x = condition, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  xlab("")+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.55, hjust = 0.5),
        legend.position = "top")
```

## By-item Analyses

### Number of Participants by Item and Condition

```{r}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ungroup() %>%
  group_by(condition, predicate_1, predicate_2) %>%
  count() %>%
  spread(condition, n) %>% 
  replace(is.na(.), 0) %>% # missing combinations of condition and predicate means no trials were collected
  kable()
```

### Pirate plots (by item)

```{r fig.width=14, fig.height=7}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = condition, y = val))+
  geom_pirate(aes(color = key, fill = key),
              violins = F, show.legend = TRUE)+
  facet_wrap(~predicate_1+predicate_2, nrow = 2)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), legend.position = "top")

```

## First Trial vs. Other Trials (for each condition)

```{r}
df.query.critical %>%
  group_by(workerid, condition, key) %>%
  mutate(first_trial  = min(chapter_num),
         last_trial = max(chapter_num),
         is_first = ifelse(chapter_num == first_trial, "first trial", 
                           "other trials")) %>%
  ggplot(., aes( x = condition, y = val))+
  geom_pirate(aes(color = key, fill = key),
              violins = F, show.legend = TRUE)+
  ylab("% Africa")+
  facet_wrap(~is_first)+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## Reaction times

*how much time do participants spend on the question slide?*

Looking only at

- AF: "Elephants live in Africa"
- AF&: "Elephants live in Africa and"
- AF&AS:  "Elephants live in Africa and Asia"

```{r}
df.query.critical %>%
  filter(key == "% live in Africa", condition %in% c('"...live in Africa __"',
                            '"...live in Africa and __"',
                                       '"...live in Africa and Asia __"')) %>%
  ggplot(., aes( x = log(rt / 1000) , color = condition, fill = condition))+
  geom_density(aes(y = ..density..), alpha = 0.3)+
  xlab("log time in seconds")
```

