---
title: "Variable Coordination by Quantifier Pilot 1"
author: "Karen Gu"
date: "6/19/2020"
output: github_document
---

This file contains preprocessing for the first pilot of the variable coordination by quantifier experiment. Raw data for this file is contained in `../../data/elephants-9/acceptability`. The experiment of this file is contained in `../../experiments/elephants-acceptability.html`. The analysis for this file is contained in `../elephants-quantifier-coord.Rmd`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(jsonlite)
library(tidyverse)
library(knitr)
```

## Subject Information

```{r load.data,  echo=F, warning=F}
data.path <- "../../data/elephants-9/acceptability/"
results.path <- data.path
anon_results = list.files(data.path)

i = 0
df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (anon_result in anon_results) {
  
  result_json = fromJSON(paste(data.path, anon_result, sep ="/"))

  df.attention = bind_rows(
    df.attention, 
    data.frame(result_json$answers$catch_trials) %>%
    mutate(
      workerid = i,
      property = gsub("\n", " ", property)
      )
  )
  
  df.subject = bind_rows(
    df.subject, 
    data.frame(result_json$answers$subject_information) %>% 
      mutate(workerid = i,
             language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))
  )
  
  df.trials = bind_rows(
    df.trials, 
    data.frame(result_json$answers$trials) %>% 
      mutate(workerid = i,
             combined_predicate = ifelse(!is.na(combined_predicate), combined_predicate, combined_precidate)) %>%
      select(workerid, kind, predicate1, predicate2, combined_predicate, trial_type, condition, response)
  )

  i = i + 1
}
```

```{r}
df.subject %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks 

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 sentences:

- Anna laughed on Jon. (coded as correct if x < 0.5)
- The train from Edmonton to Orlando was late. (coded as correct if x > 0.5)
- The burning candle spelled wrong. (coded as correct if x < 0.5)

Most participants judged the third sentence to be acceptable, so we don't exclude any participants who did so.
```{r}
df.attention %>%
  filter(condition == "practice", sentence == "The burning candle spelled wrong.") %>%
  ggplot(aes(x = response)) +
    geom_histogram() +
    labs(title = "Acceptability Ratings for 'The burning candle spelled wrong.'",
         x = "Acceptability Rating",
         y = "Number of Participants")
```

```{r}
df.slider_check <- df.attention %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    sentence == "Anna laughed on Jon." ~ response < 0.5,
    sentence == "The train was late this morning." ~ response > 0.5,
    sentence == "The burning candle spelled wrong." ~ TRUE
  )) 

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>% 
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 3
  )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

df.slider_check %>% 
  group_by(workerid) %>%
  summarize(n_correct = sum(correct)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

df.slider_check %>% 
  group_by(sentence) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall seeing from a list of 10 (5 true, 5 distractor).

```{r}
df.mmry <- df.attention %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes(x = n_correct))+
  geom_bar()+
  xlab("Number of Statements Correctly Recognized (or Correctly Rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("Number of Participants")
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attention %>%
  filter(correct == -1) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

bad.expln <- c()

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

## Participants

### Included/Excluded Subject Numbers
Removing participants who didn't get the first two sliders and who answered less than 7 of the memory check questions correctly.

```{r}
df.trials <- df.trials %>%
  mutate(memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders,
      bad_expln  = workerid %in% bad.expln) %>%
  left_join(., 
      df.mmry %>% select(workerid, n_correct)
)

df.trials %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln) %>%
  mutate(include = !memory_fail & !slider_fail) %>%
  group_by(memory_fail, slider_fail, include) %>% count() %>% kable()

df.query <- df.trials %>%
  filter(!memory_fail, !slider_fail) %>%
  rename(quantifier = trial_type, coordination = condition) %>%
  mutate(quantifier = factor(quantifier, levels = c("generic", "most", "all"), ordered = TRUE))

write.csv(df.query, 'elephants-quantifier-coord-acceptability.csv')
```
