---
title: "Variable Coordination Pilot 2"
author: "Karen Gu"
date: "4/27/2020"
output: github_document
---

# Variable Coordination Level Experiment

- This file contains pre-processing for the second pilot of the variable coordination level experiment.
- The experiment files are named `elephants-coord`. Raw data is contained in `../data/elephants-coord-rep`, Analysis for this file is contained in `./elephants-coord.Rmd`.
- n = 54 (04/27/2020)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(jsonlite)
library(gridExtra)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(broom)
library(tidybayes)
library(modelr)
theme_set(theme_few())
data.path <- "../../data/elephants-coord-rep/"
```

## Loading Data

```{r}
result.files <- list.files(data.path, pattern="json")

df.subj <- data.frame()
df.trials <- data.frame()
df.attn <- data.frame()

for (result_file in result.files) {
  
  result_json = fromJSON(paste(data.path, result_file, sep ="/"))
  worker.id = result_json$WorkerId
  condition = result_json$answers$condition

  df.attn = bind_rows(
    df.attn,
    data.frame(result_json$answers$catch_trials) %>%
      mutate(workerid = worker.id)
  )

  df.subj = bind_rows(
    df.subj,
    data.frame(result_json$answers$subject_information) %>%
      mutate(
        workerid = worker.id,
        language = gsub("\"", "", language),
        enjoyment = gsub("\"", "", enjoyment),
        age = gsub("\"", "", age),
        gender = gsub("\"", "", gender),
        problems = gsub("\"", "", problems),
        comments = gsub("\"", "", comments),
      )
  )

  df.trials = bind_rows(
    df.trials,
    data.frame(result_json$answers$trials) %>%
      mutate(
        workerid = worker.id, 
        condition = condition, 
      )
  )
}
```


## Subject Information

```{r}
df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- cats get cancer (coded as correct if x < 0.75) [being generous with this one]
- lions lay eggs (coded as correct if x < 0.10)

```{r}
df.slider_check <- df.attn %>%
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ TRUE,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  ))

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>%
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 4,
    not_three_correct = n_correct < 3
  )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

df.slider_check %>%
  group_by(workerid) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

df.slider_check %>%
  group_by(property) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.

```{r}
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`,
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits)

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1 | is.na(correct)) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

### Exclusions

These exclusions are manually coded by looking through participants explanations and prevalence ratings. Participants who gave the same prevalence rating across trials, without using the full range provided, are noted.

```{r}
workers.bad.expln <- c('bec83fc61d00a7d4ffa3b946951a2e70', '3a7dd723f40fed7a0a383a069939343d', '4bc289a226eaf2ebed9a6f266ed21cb1', '119b8973de0826f10b078c559732ccb5', 'e2ae41e9b9346ca4ea2e59c1a0501329', 'd8413cc35a0124e58fb9594da7aaf179', '3a9e470cb2caf2c71de688ffe8ffe959', '765cdd58c0e4dc60cb61beaedf2cf9c8', '956fd002ea95bbd4d212530f6e982185', '0cf23b5795a4be0cd3092a670f413cb2', '65b7c457a1fca600cb3ab0d0129ccb21', '89b1607270f1c539f8e372967b779c24', 'fd5048577f56504208c368c3bd702034', 'b28ee0d4be8559414380bdd754c773ec', '2f09bb178d82d57ee9e98784da1bb16f', '1eb3ec9876cc6a17bbae44d4761137d3', '504aa8560363dc18f9b1095cf6407c35', '02c9b466a8218e0431007a14d7054500', '75b0624edb002bc35f9a8b8be60d6dd4', 'da5013b7c30b3d20264f36989fbe4ac3', 'b7ca4e22ce73506ccb019c3113166247', 'e6532b573753e96d9385d652aba8da12', 'a3623ffaecf1e89cbe218cd459dbc6e5', '9d7e9117678074c390bfb883475724ad', '645a6517e313390917505e79b3797f3b', '9c069c5790858cfb00c23bacc10f1e95', '2b5794d92119d7e92d115695bf207170', '84cf0e42557990a784ef998dd8af955e', '01da851ac67defcef8b30d7b34765075', '9b53fbf4be0e9dc0ecb5db3222388b55', 'f64e240c246dda2026c269b105a7fa18', '920e94362bfd486741373e3f22a37fae', 'd40cc09b913fc992a03f89ff58ce036b', 'c7cd887f367d429fc95be745baea3039', '1ff677d9263a4dc0b9bd82481bf45c47', '130868e2258ca5112789154b314994c3', '44a97c6d2adae4bd4003da78c286ff5c', 'b12752e3dcbff696bf4ab9efb28bf5c4', '7fb721a8748660a36b0bf33d07b465f2', '8caf8d405cf4552c1fec1397341699ca', '60efd6cd3f3b1ef22e249845f3bbdcfe', '8a35442a3777f2c456f729e8b9559022', '45456924d6df6c4535e39857e87f7190', '730cc415993d5d65ab0e3b16c71eeb14', 'eea3a419fad867bc8c5ca38bffa3dd3d')
workers.bad.ratings <- c('351b702d37553c2576276b02684bdff0', '51db9191ad3c7a7a8ef897891360f578', 'ed5dd04a85b58e5266067c40ee228267') # coded manually by looking at the prevalence estimates given
```

## Participants

```{r}
df.trials <- left_join(
  df.trials %>%
    mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders,
      bad_expln = workerid %in% workers.bad.expln,
    ),
  df.mmry %>% select(workerid, n_correct))

df.query <- df.trials %>%
  mutate(
    memory_fail = workerid %in% workers.fail.memory,
    slider_fail = workerid %in% workers.fail.sliders,
    bad_expln = workerid %in% workers.bad.expln,
    bad_ratings = workerid %in% workers.bad.ratings,
  )
```

### Prevalence Estimates by Participant

Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.
* fill = number of correct responses on the memory check (out of 10)
* facet = participants

```{r}
df.query  %>%
  filter(!memory_fail, !slider_fail, !bad_expln) %>%
  gather(key, val, response1:response2) %>%
  ggplot(., aes( x = val, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid, ncol=3)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

### Included/Excluded Subject Numbers

Removing participants who got fewer than 7 correct on memory check and didn't get all 3 sliders, as well as participants that gave bad explanations or gave the same prevalence ratings to all sentences.

```{r}
df.query %>% write.csv('elephants-coord-20200427.csv')

df.query %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln, bad_ratings) %>%
  group_by(memory_fail, slider_fail, bad_expln) %>% count() %>% arrange(desc(n)) %>% kable()
```