---
title: "Mutual Exclusivity Pilot 1"
author: "Karen Gu"
date: "5/19/2019"
output: github_document
---

# Mutual Exclusivity Norming Experiment

This file contains pre-processing for the mutual exclusivity norming pilot. Raw data for this file is contained in `../../data/elephants-10`. Analysis for this file is contained in `../elephants-me.Rmd`.
- n = 36 (05/19/2019), n = 20 (05/20/2019)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=10)
library(tidyverse)
library(jsonlite)
library(knitr)
```

```{r load.data}
data.path <- "../../data/elephants-10/"
result.files <- list.files(data.path, pattern="json")

df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (result_file in result.files) {
    
  result_json = fromJSON(paste(data.path, result_file, sep ="/"))
  worker.id = result_json$WorkerId
  condition = result_json$answers$condition
  
  df.attention = bind_rows(
    df.attention, 
    data.frame(result_json$answers$catch_trials) %>%
      mutate(workerid = worker.id)
  )
    
  df.subject = bind_rows(
    df.subject, 
    data.frame(result_json$answers$subject_information) %>% 
      mutate(
        workerid = worker.id,
        language = gsub("\"", "", language),
        enjoyment = gsub("\"", "", enjoyment),
        age = gsub("\"", "", age),
        gender = gsub("\"", "", gender),
        problems = gsub("\"", "", problems),
        comments = gsub("\"", "", comments)
      ) 
  )
    
  df.trials = bind_rows(
    df.trials, 
    data.frame(result_json$answers$trials) %>%
      select(-main_text, -kind, -continuation, -properties, -nme_property, -property) %>%
      mutate(workerid = worker.id,
             property1 = result_json$answers$trials$property$property1$singular,
             property2 = result_json$answers$trials$property$property2$singular,
             kind = result_json$answers$trials$kind$plural,
             )
  )
}
```


### Subject Information

```{r subj.info}
df.subject %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

### Subject Exclusions

#### Practice Sliders

Exclude subjects that do not answer all 4 sliders correctly.  
- Suppose there is a dog that is a pet. What are the chances that it has a collar? coded as correct if prevalence > 0.5  
- Suppose there is an elephant that lives in Africa. What are the chances that it lives in Asia? coded as correct if prevalence < 0.1  
- What percentage of birds do you think are male? coded as correct if 0.3 < prevalence < 0.7  
- What percentage of lions do you think lay eggs? coded as correct if prevalence < 0.1

```{r slider.practice}
df.attention <- df.attention %>%
  mutate(correct = as.logical(correct)) %>%
  mutate(correct = if_else(
         str_detect(property, "dog"),
         response > 0.5,
         correct))

df.sliders <- df.attention %>%
  filter(condition == "practice") %>% 
  group_by(workerid) %>%
  summarise(
    n_correct = sum(correct)
  )

workers.fail.sliders <- df.sliders %>%
  filter(n_correct < 4) %>%
  pull(workerid)

df.sliders %>% kable()
df.attention %>%
  filter(condition =="practice") %>% 
  group_by(property) %>%
  summarise(n_correct = sum(correct)) %>%
  kable(.)
```

#### Memory Check

Exclude subjects that do not correctly identify 7 out of 10 memory check items.

```{r memory.check}
df.memory <- df.attention %>%
  filter(condition == "memory_check") %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.memory %>%
  filter(n_correct < 7) %>%
  pull(workerid)

ggplot(df.memory, aes( x = n_correct ))+
  geom_bar()+
  xlab("Number Correct")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("Number of Participants")
```

#### Task Explanations

Participants that give bad explanations are generally eliminated by one of the other exclusion criteria, so no participants are excluded solely on the basis of their explanations.

```{r}
df.explanation <- df.attention %>%
  filter(condition == "explanation") %>%
  left_join(df.sliders %>% select(workerid, n_correct) %>% rename(n_correct_sliders = n_correct)) %>%
  left_join(df.memory %>% select(workerid, n_correct) %>% rename(n_correct_memory = n_correct))

df.explanation %>%
  select(workerid, n_correct_sliders, n_correct_memory, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

#### Total Exclusions

```{r}
workers.to.exclude <- unique(c(workers.fail.memory, workers.fail.sliders))
df.query <- df.trials %>%
  filter(!(workerid %in% workers.to.exclude)) %>%
  select(-title, -type, -memory, -query) %>%
  filter(conditional_probability_me >= 0, conditional_probability_nme >= 0, marginal_probability >= 0)

write.csv(df.query, 'elephants-me-20190519.csv')
```

We exclude `r length(workers.to.exclude)` workers, leaving `r nrow(df.query)` trials for analysis.
