---
title: "Variable Coordination by Quantifier Pilot 2"
author: "Karen Gu"
date: "6/19/2020"
output: html_document
---

This file contains preprocessing for the second pilot of the variable coordination by quantifier experiment. Raw data for this file is contained in `../../data/elephants-9/truth`. The experiment of this file is contained in `../../experiments/elephants-tvjt.html`. The analysis for this file is contained in `../elephants-quantifier-coord.Rmd`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(jsonlite)
library(tidyverse)
library(knitr)
```

## Subject Information

```{r, echo=F, warning=F}
data.path <- "../../data/elephants-9/truth/"
results.path <- data.path
anon_results = list.files(data.path)

i = 0
df.subject <- data.frame()
df.trials <- data.frame()
df.attention <- data.frame()
for (anon_result in anon_results) {

  result_json = fromJSON(paste(data.path, anon_result, sep ="/"))

  df.attention = bind_rows(
    df.attention,
    data.frame(result_json$answers$catch_trials) %>%
    mutate(
      workerid = i,
      property = gsub("\n", " ", property)
      )
  )

  df.subject = bind_rows(
    df.subject,
    data.frame(result_json$answers$subject_information) %>%
      mutate(workerid = i,
             language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))
  )

  df.trials = bind_rows(
    df.trials,
    data.frame(result_json$answers$trials) %>%
      mutate(workerid = i,
             combined_predicate = ifelse(!is.na(combined_predicate), combined_predicate, combined_precidate)) %>%
      select(workerid, kind, predicate1, predicate2, combined_predicate, trial_type, condition, response)
  )

  i = i + 1
}
```

```{r}
df.subject %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```
## Attention Checks

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 sentences:

- There are ten continents on Earth. (coded as correct if response == false)
- Firefighters work on boats. (coded as correct if response == false)
- The sun rises in the east. (coded as correct if response == true)

```{r}
df.slider_check.workers <- df.attention %>%
  group_by(workerid) %>%
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 3
  )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

# number of participants that got a certain number of properties correct
df.attention %>%
  filter(condition == "practice") %>%
  group_by(workerid) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

# number of participants that got each property correct
df.attention %>%
  filter(condition == "practice") %>%
  group_by(sentence) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall seeing from a list of 10 (5 true, 5 distractor).

```{r}
df.mmry <- df.attention %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`,
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits)

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes(x = n_correct))+
  geom_bar()+
  xlab("Number of Statements Correctly Recognized (or Correctly Rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("Number of Participants")
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attention %>%
  filter(correct == -1) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

bad.expln <- c()

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

## Participants

### Included/Excluded Subject Numbers
Removing participants who didn't get the first two sliders and who answered less than 7 of the memory check questions correctly.

```{r}
df.trials <- df.trials %>%
  mutate(memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders,
      bad_expln  = workerid %in% bad.expln) %>%
  left_join(.,
      df.mmry %>% select(workerid, n_correct)
)

df.trials %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln) %>%
  mutate(include = !memory_fail & !slider_fail) %>%
  group_by(memory_fail, slider_fail, include) %>% count() %>% kable()

df.query <- df.trials %>%
  filter(!memory_fail, !slider_fail) %>%
  rename(quantifier = trial_type, coordination = condition) %>%
  mutate(quantifier = factor(quantifier, levels = c("generic", "most"), ordered = TRUE)) %>%
  mutate(coordination = factor(coordination, levels = c("np", "vp"), ordered = TRUE)) %>%
  mutate(response = response == "true")
```

### Number of Participants by Item and Condition

```{r}
df.full.tab.item.count <- df.query %>%
  group_by(coordination, quantifier, combined_predicate) %>%
  count() %>%
  spread(quantifier, n)

df.full.tab.item.count %>% kable()

df.full.tab.item.count %>%
  gather(quantifier, n, generic, most) %>%
  group_by(coordination) %>%
  summarize(n = sum(n)) %>% kable()
```

### Confidence Intervals by Coordination and Quantifier (collapsed across item)

```{r}
df_sample <- function(i) {
  df.query %>%
    group_by(quantifier, coordination) %>%
    sample_frac(replace = TRUE) %>%
    group_by(quantifier, coordination, response) %>%
    count() %>%
    group_by(quantifier, coordination) %>%
    mutate(prop = n/sum(n), sample = i) %>%
    filter(response == TRUE)
}
df_resampled <- map_df(1:10, df_sample)
df_ci <- df_resampled %>%
  group_by(coordination, quantifier) %>%
  summarise(mean = mean(prop), ci_lower = ci_lower(prop), ci_upper = ci_upper(prop))

ggplot(df_ci) +
  geom_col(aes(x = quantifier, y = mean, fill = quantifier)) +
  geom_linerange(aes(x = quantifier, ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(~ coordination) +
  scale_fill_manual(values = c("#4477AA", "#CC6677"), guide = FALSE) +
  ylab("Proportion `True` Responses") +
  xlab("Quantifier")

ggsave("~/Documents/talks/1906-xprag-elephants/truthJudgment_NP_VP.pdf", width = 5, height = 3.5)
```

### Model

```{r}
contrasts(df.query$coordination) <- contr.sum
contrasts(df.query$quantifier) <- contr.sum
recall_glm <- glmer(response ~ coordination * quantifier + (1 | workerid) + (1 | combined_predicate),
                  data = df.query,
                  family = "binomial")
summary(recall_glm)
```

## By-item Analyses

### Number of Trials by Item and Quantifier

write.csv(df.query, 'elephants-quantifier-coord-truth.csv')
```
