---
title: "elephants-1-cogsci2019"
author: "MH Tessler"
date: "1/17/2019"
output: github_document
---

[Link to experiment](http://www.mit.edu/~tessler/projects/elephants/experiments/elephants-3.html)

## Experiment 1 for CogSci 2019 (Elephants-3i)

### Changes from Pilot 3

- interrupted version of experiment 3 (some trials ask questions mid-chapter)
- added trials where we ask about non-mutually exclusive properties (NME)
- randomize order of trials with constraint that no 2 criticals back-to-back

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(ggpirate)
library(jsonlite)
library(gridExtra)
library(lme4)
theme_set(theme_few())
data.path <-"../../data/elephants-3i/"
```

##
```{r}
result.files <- list.files(data.path, pattern="json")
  newdata.subject <- data.frame()
  newdata.trials <- data.frame()
  newdata.attention <- data.frame()
  for (result_file in result.files) {
    
    result_json = fromJSON(paste(data.path, result_file, sep ="/"))
    worker.id = result_json$WorkerId
    condition = result_json$answers$condition
  
    newdata.attention = bind_rows(
      newdata.attention, 
      data.frame(result_json$answers$catch_trials) %>%
        mutate(workerid = worker.id)
    )
    
    newdata.subject = bind_rows(
      newdata.subject, 
      data.frame(result_json$answers$subject_information) %>% 
        mutate(workerid = worker.id,
               language = gsub("\"", "", language),
           enjoyment = gsub("\"", "", enjoyment),
           age = gsub("\"", "", age),
           gender = gsub("\"", "", gender),
           problems = gsub("\"", "", problems),
           comments = gsub("\"", "", comments)) 
    )
    
    newdata.trials = bind_rows(
      newdata.trials, 
      data.frame(result_json$answers$trials) %>%
        mutate(workerid = worker.id, condition = condition)
    )
  }
```


## Subject Information

```{r}
df.subj <- bind_rows(newdata.subject, read_csv(
  paste(data.path, "elephants-3i-subject_information.csv", sep = "")
  ) %>%
  mutate(language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments),
         workerid = as.character(workerid)))

df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks 

### Slider Practice

Before the experiment, participants practice using the sliders to rate 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- birds are male (coded as correct if 0.25 < x < 0.75)
- cats get cancer (coded as correct if x < 0.75) [being generous with this one]
- lions lay eggs (coded as correct if x < 0.10)

```{r}
df.attn <- bind_rows(newdata.attention, read_csv(
  paste(data.path, "elephants-3i-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition),
         workerid = as.character(workerid),
         correct = case_when(correct == "true" ~ 1,
                             correct == "false" ~ 1,
                             correct == "1" ~ 1,
                             correct == "0" ~ 0)))

# slider bar check

df.slider_check <- df.attn %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 & response < 0.75,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  )) 

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>% 
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 4,
    not_three_correct = n_correct < 3
    )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

# number of participants grouped by number of correct sliders
df.slider_check %>% 
  group_by(workerid) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

# number of correct responses grouped by slider question
df.slider_check %>% 
  group_by(property) %>%
  summarize(n_correct = sum(correct, na.rm = TRUE)) %>%
  kable()
```

### Memory Check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.
```{r}
# memory check data
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")
```

### Slider Practice and Memory Check

```{r}
df.mmry %>%
  select(workerid, n_correct) %>%
  left_join(df.slider_check.workers %>% select(workerid, n_correct), by=c("workerid")) %>%
  rename(n_correct_memory = n_correct.x, n_correct_slider = n_correct.y) %>%
  ggplot() +
  geom_count(aes(x = n_correct_memory, y = n_correct_slider))
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1 | is.na(correct)) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

### Exclusions

Subject 12 rated 66% cats get cancer, otherwise seems proficient. In other subjects, attention check mechanisms seem correlated.

```{r}
workers.to.exclude <- unique(c(workers.fail.memory, workers.fail.sliders))
workers.to.exclude <- workers.to.exclude[workers.to.exclude != 12]
```

## Participants

```{r}
df.trials <- left_join(
  bind_rows(newdata.trials,
    read_csv(
    paste(data.path, "elephants-3i-trials.csv", sep = "")
    ) %>% mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      quantifier = gsub("\"", "", quantifier),
      workerid = as.character(workerid)
      )) %>% 
    mutate(
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders
    ),
  df.mmry %>% select(workerid, n_correct))

df.query <- df.trials %>%
  filter(page_type == "query") %>%
  gather(key, val, response_1, response_2)
```

### Included/Excluded Subject Numbers

Removing participants who got fewer than 7 correct on memory check and didn't get all 4 sliders. (Participants with bad explanations usually fell into one of these other groups.)

```{r}
df.query %>%
  distinct(workerid, memory_fail, slider_fail, bad_expln) %>%
  group_by(memory_fail, slider_fail) %>% count() %>% kable()
```

### Prevalence Estimates by Participant
 
Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.
* fill = number of correct responses on the memory check (out of 10)
* facet = participants

```{r}
df.query  %>%
  ggplot(., aes( x = val, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## Filler Trials

These used quantifiers (and thus we have strong idea about literal meaning).

```{r}
df.query.filler <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num, 
         rt, trial_type, quantifier, page_type, key, val)

df.query.filler  %>%
  ggplot(., aes( x = val ))+
  geom_histogram(aes(y = ..density.. *0.05, binwidth = 0.05))+
  ylab("Proportion") +
  facet_grid(condition~quantifier)
```

## Critical Trials (collapsed across item)

## Histograms of Prevalence Estimates by Condition (collapsed across item)
```{r}
df.query.critical <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, predicate_2, 
         key, val, page_type, memory_fail, slider_fail, chapter) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(condition = factor(condition, 
                            levels = c("interrupted", 
                                       "uninterrupted",
                                       "nme_interrupted",
                                       "nme_uninterrupted"),
                            labels = c('"...live in Africa __"\nQ(Asia)',
                                       '"...and Asia"\nQ(Asia)',
                                       '"...live in Africa __"\nQ(bugs)',
                                       '"...and eat bugs"\nQ(bugs)')),
         key = factor(key, levels = c("response_1", "response_2"),
                      labels = c("% Africa", "% Asia / bugs"))) %>%
  mutate(me = if_else(str_detect(condition, "bugs"), "nme", "me"),
         interrupted = if_else(str_detect(condition, "and"), "uninterrupted", "interrupted"))

df.query.critical %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(key~condition)
```

### Mutual Exclusivity

```{r}
df.query.critical %>%
  spread(key, val) %>%
  mutate(mutually_exclusive = `% Africa` + `% Asia / bugs` <= 1.00) %>%
  group_by(condition) %>%
  tidyboot_mean(column = mutually_exclusive) %>%
  ggplot(aes(x = condition, y = mean, ymin = ci_lower, ymax = ci_upper)) +
  geom_col() +
  geom_errorbar(position = position_dodge(0.8), width = 0.3, color = "red") +
  ylab("Proportion Mutually Exclusive Responses")
```

### Bootstrapped 95% Confidence Intervals (collapsed across item)

```{r}
df.bs.query.critical <- df.query.critical %>%
  group_by(me, interrupted, key, condition) %>%
  tidyboot_mean(column = val) %>%
  ungroup()

df.bs.query.critical %>%
  ggplot(., aes( x = interrupted, fill = key, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  facet_wrap(~me)
```

### Pirate Plots (collapsed across item)
```{r}
ggplot(df.bs.query.critical, aes( x = interrupted, fill = key))+
  #theme_black()+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5, color = 'white')+

  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, 
           alpha = 0.5, 
           color = 'white')+
  geom_point(data = df.query.critical, position = position_jitterdodge(),
             inherit.aes = F, aes(x = interrupted, y = val, color = key), 
             alpha = 0.5)+
    geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2,
                color = 'white')+  
  ylab("Implied prevalence rating")+
  facet_wrap(~ me) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(#axis.text.x = element_text(angle = 30, vjust = 0.55, hjust = 0.5),
        legend.position = "top")

#ggsave("~/Documents/talks/coglunch-0319/figs/elephants-expt1.pdf", 
#       width = 6, height = 4)

#ggsave(paste(fig.path, "expt2_summary.pdf", sep = ""), height = 4.5, width = 5.5)
```

```{r}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = condition, y = val))+
  geom_pirate(aes(color = key, fill = key),
              violins = F, show.legend = TRUE)+
  ylab("% Africa")+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### ME vs. NME Questions

```{r}
df.bs.query.critical.asia <- df.bs.query.critical %>%
  filter(condition %in% c("\"...live in Africa __\"\nQ2(Asia)",
                          "\"...live in Africa and Asia\"\nQ2(Asia)")) %>%
  mutate(
        key = as.character(key),
second_query = "Question 2: % live in Asia",
         key = ifelse(as.character(key) == "% property 2", "% live in Asia", key))

df.query.critical.asia <- df.query.critical %>%
  filter(condition %in% c("\"...live in Africa __\"\nQ(Asia)",
                          "\"...live in Africa and Asia\"\nQ(Asia)")) %>%
  mutate(
    key = as.character(key),
    second_query = "Question 2: % live in Asia",
         key = ifelse(key == "% property 2", "% live in Asia", key))


fig.expt1a <- ggplot(df.bs.query.critical.asia, aes( x = condition, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(data = df.query.critical.asia, position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = key), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
      scale_fill_solarized()+
    scale_color_solarized()+
  facet_wrap(~second_query)+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.55, hjust = 0.5),
        legend.position = "right")


df.bs.query.critical.bugs <- df.bs.query.critical %>%
  filter(!(condition %in% c("\"...live in Africa __\"\nQ2(Asia)",
                          "\"...live in Africa and Asia\"\nQ2(Asia)"))) %>%
  mutate(
        key = as.character(key),
second_query = "Question 2: % eat bugs",
         key = ifelse(as.character(key) == "% property 2", "% eat bugs", key),
      key = factor(key, levels = c("% live in Africa", "% eat bugs")))

df.query.critical.bugs <- df.query.critical %>%
  filter(!(condition %in% c("\"...live in Africa __\"\nQ2(Asia)",
                          "\"...live in Africa and Asia\"\nQ2(Asia)"))) %>%
  mutate(
    key = as.character(key),
    second_query = "Question 2: % eat bugs",
         key = ifelse(key == "% property 2", "% eat bugs", key),
      key = factor(key, levels = c("% live in Africa", "% eat bugs")))


fig.expt1b <- ggplot(df.bs.query.critical.bugs, aes( x = condition, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(data = df.query.critical.bugs, position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = key), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  facet_wrap(~second_query)+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 30, vjust = 0.55, hjust = 0.5),
        legend.position = "right")

cowplot::plot_grid(
  fig.expt1a, fig.expt1b, labels = c("A", "B"),
  nrow = 1
)
```

## By-item Analyses

### Items
Items can be categorized by the continuation type and the coordination type.  

* continuation type: the interrupted sentence containing the questioned properties varies according to how real the subject matter is.  
    + real: Sentence and properties are completely real.  
    + fakeNames: The properties concern real items (like religion), but the name is made-up (Daith).  
    + fakeDefs: The properties concern completely made-up items.  
* coordination type: the "and" conjoins different syntactic categories  

```{r}
items <- fromJSON("./items-1.json")
items %>%
  group_by(coordination, continuationType) %>%
  count() %>%
  kable()
```

### Number of participants by Item and Condition

```{r}
df.query %>%
  filter(!memory_fail, !slider_fail, trial_type == "critical") %>%
  group_by(condition, predicate_1, predicate_2) %>%
  count() %>%
  spread(condition, n) %>% 
  replace(is.na(.), 0) %>% # missing combinations of condition and predicate means no trials were collected
  kable()
```

### Pirate Plots (by item)

```{r fig.width=10, fig.height=15}
me <- df.query.critical %>%
  filter(me == "me")  %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = interrupted, fill = interrupted),
              violins = F, show.legend = TRUE, bars =T)+
  facet_wrap(~predicate_1+predicate_2, nrow = 2)+
  ylab("%")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), legend.position = "top") +
  ggtitle("ME Questions")

nme <- df.query.critical %>%
  filter(me == "nme")  %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = interrupted, fill = interrupted),
              violins = F, show.legend = TRUE, bars =T)+
  facet_wrap(~predicate_1+predicate_2, nrow = 2)+
  ylab("%")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), legend.position = "top") +
  ggtitle("NME Questions")

grid.arrange(me, nme, nrow = 2)
```

### Mutual Exclusivity (by item)

```{r}
# loading data from elephants-10
data.path.me <- "../../data/elephants-10/"
result.files.me <- list.files(data.path.me, pattern="json")

df.subject.me <- data.frame()
df.trials.me <- data.frame()
df.attention.me <- data.frame()
for (result_file in result.files.me) {
    
  result_json = fromJSON(paste(data.path.me, result_file, sep ="/"))
  worker.id = result_json$WorkerId
  condition = result_json$answers$condition
  
  df.attention.me = bind_rows(
    df.attention.me, 
    data.frame(result_json$answers$catch_trials) %>%
      mutate(workerid = worker.id)
  )
    
  df.subject.me = bind_rows(
    df.subject.me, 
    data.frame(result_json$answers$subject_information) %>% 
      mutate(
        workerid = worker.id,
        language = gsub("\"", "", language),
        enjoyment = gsub("\"", "", enjoyment),
        age = gsub("\"", "", age),
        gender = gsub("\"", "", gender),
        problems = gsub("\"", "", problems),
        comments = gsub("\"", "", comments)
      ) 
  )
    
  df.trials.me = bind_rows(
    df.trials.me, 
    data.frame(result_json$answers$trials) %>%
      select(-main_text, -continuation, -kind, -properties, -nme_property, -property) %>%
      mutate(workerid = worker.id,
             property1 = result_json$answers$trials$property$property1$singular,
             property2 = result_json$answers$trials$property$property2$singular
             )
  )
}

df.attention.me <- df.attention.me %>%
  mutate(correct = as.logical(correct)) %>%
  mutate(correct = if_else(
         str_detect(property, "dog"),
         response > 0.5,
         correct))

df.sliders.me <- df.attention.me %>%
  filter(condition == "practice") %>% 
  group_by(workerid) %>%
  summarise(
    n_correct = sum(correct)
  )

workers.fail.sliders.me <- df.sliders.me %>%
  filter(n_correct < 4) %>%
  pull(workerid)

df.memory.me <- df.attention.me %>%
  filter(condition == "memory_check") %>%
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory.me <- df.memory.me %>%
  filter(n_correct < 7) %>%
  pull(workerid)

workers.to.exclude.me <- unique(c(workers.fail.memory.me, workers.fail.sliders.me))
df.query.me <- df.trials.me %>%
  filter(!(workerid %in% workers.to.exclude)) %>%
  select(-type, -memory, -query)
```

## Mutual Exclusivity Comparison (Expt1 and Elephants-10)

### ME

```{r fig.height = 12}
df.query.critical.mesumm <- df.query.critical %>%
  filter(me == "me", interrupted == "uninterrupted") %>%
  spread(key, val) %>%
  mutate(total = `% Africa` + `% Asia / bugs`) %>%
  group_by(predicate_1, chapter) %>%
  summarise(avg_total = mean(total))

ggplot(df.query.critical.mesumm, aes(x = predicate_1, y = avg_total)) +
  geom_text(aes(label = predicate_1)) +
  ylab("Mean Total Prevalence (%Africa + %Asia)") +
  xlab("") +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())
```

```{r}
df.probs.me <- df.query.me %>%
  group_by(property1, title) %>%
  summarise(mean_conditional = mean(conditional_probability_me),
         mean_marginal = mean(marginal_probability),
         joint_estimate = mean_conditional*mean_marginal)

df.query.critical.mesumm %>%
  left_join(df.probs.me, by = c("chapter" = "title")) %>%
  ggplot(aes(x = avg_total, y = joint_estimate)) +
  geom_text(aes(label = property1)) +
  xlab("Mean Total Prevalence (%Africa + %Asia)") +
  ylab("Joint Probability (% Africa and Asia)")
```

### NME

```{r fig.height=12}
df.query.critical.nmesumm <- df.query.critical %>%
  filter(me == "nme", interrupted == "uninterrupted") %>%
  spread(key, val) %>%
  mutate(total = `% Africa` + `% Asia / bugs`) %>%
  group_by(predicate_1, chapter) %>%
  summarise(avg_total = mean(total))

ggplot(df.query.critical.nmesumm, aes(x = predicate_1, y = avg_total)) +
  geom_text(aes(label = predicate_1)) +
  ylab("Mean Total Prevalence (%Africa + %eat bugs)") +
  xlab("") +
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())
```

```{r}
df.probs.nme <- df.query.me %>%
  group_by(property1, title) %>%
  summarise(mean_conditional = mean(conditional_probability_nme),
         mean_marginal = mean(marginal_probability),
         joint_estimate = mean_conditional*mean_marginal)

df.query.critical.mesumm %>%
  left_join(df.probs.nme, by = c("chapter" = "title")) %>%
  ggplot(aes(x = avg_total, y = joint_estimate)) +
  geom_text(aes(label = property1)) +
  xlab("Mean Total Prevalence (%Africa + %eat bugs)") +
  ylab("Joint Probability (% Africa and eat bugs)")
```

### Pirate Plots (by Coordination)

```{r fig.width=14, fig.height=7}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  left_join(select(items, property1, property2, continuationType, coordination), by = c("predicate_1" = "property1", "predicate_2" = "property2")) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F, show.legend = TRUE)+
  facet_wrap(~coordination)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### Pirate Plots (by Realness)

```{r fig.width=14, fig.height=7}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  left_join(select(items, property1, property2, continuationType, coordination), by = c("predicate_1" = "property1", "predicate_2" = "property2")) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F, show.legend = TRUE)+
  facet_wrap(~continuationType)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

## Order Effects

## First vs. Second Half
```{r fig.height=7}
max.chapter <- max(df.query.critical$chapter_num)

df.query.blocked <- df.query.critical %>%
  mutate(half = case_when(
    chapter_num <= max.chapter %/% 2 ~ "first",
    TRUE ~ "second"))

df.query.blocked %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = interrupted, fill = interrupted),
              violins = F, show.legend = TRUE, bars =T)+
  ylab("%")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1), legend.position = "top") +
  facet_grid(me~half)
```

### First Trial

```{r}
df.query.critical %>%
  group_by(workerid, condition, key) %>%
  mutate(first_trial  = min(chapter_num),
         is_first = chapter_num == first_trial) %>%
  filter(is_first) %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(condition~key)+
  theme(strip.text.y = element_text(angle = 0))+
  xlim(0, 1)
```

## Reaction Times

*how much time do participants spend on the question slide?*

```{r}
df.query.critical %>%
  filter(key == "% Africa") %>%
  ggplot(., aes( x = log(rt / 1000) , color = condition, fill = condition))+
  geom_density(aes(y = ..density..), alpha = 0.3)+
  xlab("log time in seconds")
```