---
title: "elephants-3i-pilot"
author: "MH Tessler"
date: "1/17/2019"
output: github_document
---

[Link to experiment](http://www.mit.edu/~tessler/projects/elephants/experiments/elephants-3.html)

### Changes from Pilot 3

- interrupted version of experiment 3 (some trials ask questions mid-chapter)
- added trials where we ask about non-mutually exclusive properties (NME)
- randomize order of trials with constraint that no 2 criticals back-to-back

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(ggpirate)
theme_set(theme_few())
project.path <- "~/projects/elephants/"
expt.prefix <- "elephants-3i"
data.path <- paste("data", expt.prefix,sep = "/")
```

### Subject information

```{r}
df.subj <- read_csv(
  paste(project.path, data.path, "/", 
        expt.prefix, "-subject_information.csv", sep = "")
  ) %>%
  mutate(language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))

df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention check 

### Slider practice

Before the experiment, participants practice usign the sliders to rate 3 category--property pairs:

- dogs bark (coded as correct if x > 0.5)
- birds are male (coded as correct if 0.25 < x < 0.75)
- cats get cancer (coded as correct if x < 0.75)
- lions lay eggs (coded as correct if x < 0.10)


### Memory check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.


```{r}
df.attn <- read_csv(
  paste(project.path, data.path, "/", 
        expt.prefix, "-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition))

# slider bar check

df.slider_check <- df.attn %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 & response < 0.75,
    property == "cats get cancer" ~ response < 0.75,
    property == "lions lay eggs" ~ response < 0.1
  )) 

df.slider_check.workers <- df.slider_check %>%
  group_by(workerid) %>% 
  summarize(
    n_correct = sum(correct),
    not_all_correct = n_correct < 4,
    not_three_correct = n_correct < 3
    )

workers.fail.sliders <- df.slider_check.workers %>%
  filter(not_all_correct) %>%
  pull(workerid)

df.slider_check %>% 
  group_by(workerid) %>%
  summarize(n_correct = sum(correct)) %>%
  group_by(n_correct) %>% count() %>%
  kable()

df.slider_check %>% 
  group_by(property) %>%
  summarize(n_correct = sum(correct)) %>%
  kable()
```


```{r}
# memory check data
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  #filter(correct != -1) %>% # remove explanations
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")

#df.mmry %>%
# kable(.)

```


### Explanations of task

```{r}
df.expln <- df.attn %>%
  filter(correct == -1) %>%
  left_join(., df.mmry %>% select(workerid, n_correct) %>%
              rename(n_memory_correct = n_correct)) %>%
  left_join(., df.slider_check.workers %>% select(workerid, n_correct) %>%
              rename(n_slider_correct = n_correct))

df.expln %>%
  select(workerid,n_slider_correct,  n_memory_correct, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

Subject 12 rated 66% cats get cancer, otherwise seems proficient. In other subjects, attention check mechanisms seem correlated.

```{r}
workers.to.exclude <- unique(c(workers.fail.memory, workers.fail.sliders))
workers.to.exclude <- workers.to.exclude[workers.to.exclude != 12]
```


## Trial data

Removing participants who got fewer than 7 correct on memory check and didn't get all 4 sliders.

```{r}
df.trials <- left_join(
    read_csv(
    paste(project.path, data.path, "/", 
          expt.prefix, "-trials.csv", sep = "")
    ) %>% 
    mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      #generic = gsub("\"", "", generic),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      #verb = gsub("\"", "", verb),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      quantifier = gsub("\"", "", quantifier),
      memory_fail = workerid %in% workers.fail.memory,
      slider_fail = workerid %in% workers.fail.sliders
      ),
    df.mmry %>% select(workerid, n_correct)
)

df.query <- df.trials %>%
  filter(page_type == "query") %>%
  gather(key, val, response_1, response_2)
```

## participant responses
 
collapsed across trials

- fill = number of correct responses on the memory check (out of 10)
- facet = particiapnts

```{r}
df.query  %>%
  ggplot(., aes( x = val, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## filler trials

these used quantifiers (and thus we have strong idea about literal meaning)

```{r}
df.query.filler <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num, 
         rt, trial_type, quantifier, page_type, key, val)

df.query.filler  %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(condition~quantifier)
```

## critical trials (collapsed across item)

```{r}
df.query.critical <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, predicate_2, 
         key, val, page_type, memory_fail, slider_fail) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(condition = factor(condition, 
                            levels = c("interrupted", 
                                       "uninterrupted",
                                       "nme_interrupted",
                                       "nme_uninterrupted")),
         key = factor(key, levels = c("response_1", "response_2"),
                      labels = c("% live in Africa", "% property 2")))

df.query.critical %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(key~condition)

unique(df.query.critical$condition)
```

#### bootstrapped 95% confidence intervals

```{r}
df.bs.query.critical <- df.query.critical %>%
  group_by(condition, key) %>%
  tidyboot_mean(column = val)

df.bs.query.critical %>%
  ggplot(., aes( x = condition, fill = key, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```


```{r}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = condition, y = val))+
  geom_pirate(aes(color = key, fill = key),
              violins = F, show.legend = TRUE)+
  #geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  #geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### By-item averages

N's per item X condition

```{r}
df.query.critical %>%
  filter(!memory_fail, !slider_fail) %>%
  ungroup() %>%
  group_by(condition, predicate_1, predicate_2) %>%
  count() %>%
  spread(condition, n) %>% kable()
```

### Pirate plots

```{r fig.width=10, fig.height=7}
df.query.critical %>%
  filter(condition %in% c("interrupted", "uninterrupted")) %>%
  filter(!memory_fail, !slider_fail) %>%
  ggplot(., aes( x = key, y = val))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F, show.legend = TRUE, bars =T)+
  #geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  facet_wrap(~predicate_1+predicate_2, nrow = 2)+
  ylab("% Africa")+
  #geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```




## first trial

```{r}
df.query.critical %>%
  group_by(workerid, condition, key) %>%
  mutate(first_trial  = min(chapter_num),
         is_first = chapter_num == first_trial) %>%
  filter(is_first) %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(condition~key)+
  theme(strip.text.y = element_text(angle = 0))+
  xlim(0, 1)
```

## Reaction times

*how much time do participants spend on the question slide?*

```{r}
df.query.critical %>%
  filter(key == "% live in Africa") %>%
  ggplot(., aes( x = log(rt / 1000) , color = condition, fill = condition))+
  #geom_histogram(aes(y = ..density..), alpha = 0.0, position = position_dodge())+
  geom_density(aes(y = ..density..), alpha = 0.3)+
  xlab("log time in seconds")
  #facet_wrap(~condition, nrow = 2)
```

