---
title: "elephants-1-pilot"
author: "MH Tessler"
date: "1/14/2019"
output: github_document
---

[Link to experiment](http://www.mit.edu/~tessler/projects/elephants/experiments/elephants-1.html)

Participants read a storybook about an alien planet. Each chapter consists of some description of a kind, for example, elephants. The participants are either asked in the middle of a chapter or at the end of the chapter what percentage of the kind they think a particular predicate applies to (for instance, what percentage of elephants do you think live in Africa?).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(ggpirate)
theme_set(theme_few())
data.path <- "../data/elephants-1/elephants-1"
```

## Subject Information

```{r}
df.subj <- read_csv(
    paste(data.path, "-subject_information.csv", sep="")
  ) %>%
  # remove quotes around subject responses
  mutate(language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))

df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention Checks

### Memory Check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor).

```{r}
df.attn <- read_csv(
    paste(data.path,"-catch_trials.csv", sep = "")
  ) %>%
  # remove quotes
  mutate(property = gsub("\"", "", property))

# memory check data
df.mmry <- df.attn %>%
  filter(correct != -1) %>% # remove explanations
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

# workers to include, by id
workerid.pass <- df.mmry %>% filter(n_correct >= 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("Correct Responses")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("Number of Participants")

df.mmry %>%
  kable(.)
```

### Explanations of Task

After the story, participants are also asked to explain generally what they did in the experiment.

```{r}
df.expln <- df.attn %>%
  filter(correct == -1) 

df.expln %>%
  select(workerid, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

## Participants

```{r}
df.trials <- left_join(
    read_csv(
    paste(data.path, "-trials.csv", sep = "")
    ) %>% 
    mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      generic = gsub("\"", "", generic),
      page_content = gsub("\"", "", page_content),
      predicate = gsub("\"", "", predicate),
      verb = gsub("\"", "", verb),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      memory_pass = workerid %in% workerid.pass
      ),
    df.mmry %>% select(workerid, n_correct)
)

df.query <- df.trials %>%
  filter(page_type == "query")
```

### Prevalence Estimates by Participant
 
Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.
* fill = number of correct responses on the memory check (out of 10)
* facet = participants

```{r fig.width = 10}
df.query  %>%
  ggplot(., aes( x = response, fill = n_correct))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## Filler Trials

For all subsequent analyses, we will only consider participants who answered 7 or more items correctly in the statement identification task. (n = `r df.mmry %>% filter(n_correct >= 7) %>% nrow() ` out of `r nrow(df.mmry)`)

In filler trials, participants read a chapter about a novel kind similar to the critical trials. They are then asked to estimate the prevalence of a property in the kind. Two of the filler trials used quantifiers (and thus we have strong idea about literal meaning)

- "all aliens love Zorxon"
- "no storms (or few) on Dax result in permanent damage..."

Other two fillers are generics about singular properties.

```{r}
df.query.dstrct <- df.query %>%
  filter(memory_pass) %>%
  filter(trial_type == "distractor") %>%
  select(workerid, condition, chapter_num, rt, trial_type, generic, page_type, response)

df.query.dstrct  %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_wrap(~generic + condition, labeller = as_labeller(label_wrap_gen(width = 40, multi_line = TRUE)))
```

## Critical Trials (collapsed across item)
Participants answered questions of the form "What percentage of elephants do you think live in Africa?" in both conditions. The x-axis shows the prevalence estimates.

```{r}
df.query.critical <- df.query %>%
  filter(memory_pass) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, generic, page_type, response, memory_pass) %>%
  filter(trial_type == "critical")

df.query.critical %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_wrap(~condition)
```

### Bootstrapped 95% Confidence Intervals (collapsed over items)

```{r fig.width = 4, fig.height = 3}
# bootstrapped 95% confidence intervals for the mean response by condition (Africa vs. Africa and Asia)
df.bs.query.critical <- df.query.critical %>%
  group_by(condition) %>%
  tidyboot_mean(column = response)

df.bs.query.critical %>%
  ungroup() %>%
  mutate(condition = factor(condition, levels = c("single", "conjunction"),
                            labels = c("..Africa", "..Africa and Asia"))) %>%
  ggplot(., aes( x = "manipulation", fill = condition, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()
```

## Critical Trials (by Item)

### Number of Trials by Item and Condition

```{r}
df.query.critical %>%
  filter(memory_pass) %>%
    ungroup() %>%
  mutate(condition = factor(condition, levels = c("single", "conjunction"),
                            labels = c("..Africa", "..Africa and Asia")),
         generic = factor(generic, levels=unique(generic[order(chapter_num)]), ordered=TRUE)) %>%
  group_by(condition, generic) %>%
  count() %>%
  spread(condition, n)
```

### By-item confidence intervals

```{r}
df.bs.crit.item <- df.query.critical %>%
  filter(memory_pass) %>%
  group_by(condition, generic, chapter_num) %>%
  tidyboot_mean(column = response)

df.bs.crit.item %>%
  ungroup() %>%
  mutate(condition = factor(condition, levels = c("single", "conjunction"),
                            labels = c("..Africa", "..Africa and Asia")),
         generic = factor(generic, levels=unique(generic[order(chapter_num)]), ordered=TRUE)) %>%
  ggplot(., aes( x = generic, fill = condition, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  xlab("item, in order of presentation from L to R")
```

### Pirate Plots (by item)

Points represent individual data points. Gray-outlined rectangles represent 95% confidence intervals.

```{r}
df.query.critical %>%
  filter(memory_pass) %>%
    ungroup() %>%
  mutate(condition = factor(condition, levels = c("single", "conjunction"),
                            labels = c("..Africa", "..Africa and Asia")),
         generic = factor(generic, levels=unique(generic[order(chapter_num)]), ordered=TRUE)) %>%
  ggplot(., aes( x = condition, fill = condition, y = response))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F)+
  facet_wrap(~generic)+
  ylab("% Africa")+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  xlab("item, in order of presentation from L to R")
```

## First Trial

"Krens ascribe to the Caboo religion...and the Daith religion."

```{r}
df.query.critical %>%
  filter(chapter_num == 3) %>% # first critical chapter after introduction chapter and first filler trial
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_wrap(~condition)
```

```{r}
df.query.critical %>%
  filter(chapter_num == 3) %>%
  group_by(condition) %>%
  tidyboot_mean(column = response) %>%
  ungroup() %>%
  mutate(condition = factor(condition, levels = c("single", "conjunction"),
                            labels = c("..Africa", "..Africa and Asia"))) %>%
  ggplot(., aes( x = "manipulation", fill = condition, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()
```

