---
title: "Mutual Exclusivity Norming Experiment"
author: "Karen Gu"
date: "5/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width=10)
library(tidyverse)
library(jsonlite)
library(knitr)
```

This file contains analysis for the mutual exclusivity norming pilot. Raw data for this file is contained in `../../data/elephants-10`. Preprocessing for this file is contained in `./preprocessing/elephants-me-20190519.Rmd`.

The experiment uses the same story as in elephants-3, without last sentence, asking explicitly about the following probabilities:  
- Pr(Africa) - marginal distribution
- Pr(Asia | Africa) - conditional distribution (ME)
- Pr(eat bugs | Africa) - conditional distribution (ME)

```{r load.data}
df.query <- read.csv('preprocessing/elephants-me-20190519.csv')
```

## Mutual Exclusivity

We see that the mutual exclusivity varies across items, where no items are perfectly correlated (Pr(Asia|Africa) = 1), but no items are perfectly anticorrelated either (Pr(Asia|Africa) = 0).

```{r fig.height=7}
df.probs <- df.query %>%
  group_by(property1) %>%
  summarise(mean_conditional = mean(conditional_probability_me),
         mean_marginal = mean(marginal_probability),
         joint_estimate = mean_conditional*mean_marginal)

ggplot(df.probs, aes(x = mean_marginal, y = mean_conditional)) +
  geom_text(aes(label = property1)) +
  xlab("Marginal Probability Pr(Africa)") +
  ylab("Conditional Probability Pr(Asia | Africa)")
```

## Marginal Probabilities

```{r}
ggplot(df.query, aes(x = marginal_probability)) +
  geom_histogram() +
  facet_wrap(~property1) +
  xlab('Pr(Africa)')
```

## Conditional Probabilities (ME)

```{r}
ggplot(df.query, aes(x = conditional_probability_me)) +
  geom_histogram() +
  facet_wrap(~property1) + 
  xlab('Pr(Asia|Africa)')
```

## Conditional Probabilities (NME)

```{r}
ggplot(df.query, aes(x = conditional_probability_nme)) +
  geom_histogram() +
  facet_wrap(~property1) +
  xlab('Pr(eat bugs|Africa)')
```

## Joint Probabilities

```{r}
df.query %>%
  mutate(joint = conditional_probability_me*marginal_probability) %>%
  ggplot(aes(x = joint)) +
  geom_histogram() +
  facet_wrap(~property1) +
  xlab('Pr(Africa and Asia)')
```

## Property Symmetry

We alternate between asking about "Africa" and "Asia" for the marginal probability. Are these symmetric?

```{r}
df.query %>%
  mutate(ask_first = if_else(ask_first, "first", "second")) %>%
  group_by(property1, property2, ask_first) %>%
  summarise(mean_marginal = mean(marginal_probability)) %>%
  spread(ask_first, mean_marginal) %>%
  ggplot(aes(x = first, y = second)) +
    geom_text(aes(label = property1)) +
    geom_abline(yintercept = 0, slope = 1)
```

It's possible that there is some effect of order, which may vary by item.