---
title: "Variable Coordination by Quantifier"
author: "Karen Gu"
date: "5/08/2019"
output: github_document
---

This file contains analysis of the variable coordination by quantifier experiment, which consists of two pilots featuring different tasks.

Pilot 1 is an acceptability task using a sliding scale (0-100%), where participants rate items of the form Elephants live in Africa and Asia.
* between-subjects: VP vs. NP coordination  
* within-subjects: generic vs. most vs. all  
* 30 trials per subject (10 generic, 10 most, 10 all)
Raw data is contained in `../data/elephants-9/`. The preprocessing file is contained in `./preprocessing/elephants-quantifier-coord-acceptability.Rmd`. The experiment is contained in `../experiments/elephants-acceptability.html`.

Pilot 2 is a TVJT using a 2-alternative forced choice, where participants rate items of the form Elephants live in Africa and Asia.
* between-subjects: VP vs. NP coordination  
* within-subjects: generic vs. most 
* 30 trials per subject (15 generic, 15 most)
Raw data is contained in `../data/elephants-9-truth/`. The preprocessing file is contained in `./preprocessing/elephants-quantifier-coord-truth.Rmd`. The experiment is contained in `../experiments/elephants-truth.html`.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(viridis)
library(tidyboot)
library(lme4)
library(brms)
library(lmerTest)
theme_set(theme_few())
```

```{r load.data}
df.query.truth <- read.csv('./preprocessing/elephants-quantifier-coord-truth.csv') %>%
  mutate(quantifier = factor(quantifier, levels = c("generic", "most"), labels = c("generic", "most")),
         coordination = factor(coordination, levels = c("np", "vp"), labels = c("np", "vp")))
df.query.acceptability <- read.csv('./preprocessing/elephants-quantifier-coord-acceptability.csv')
```


## Number of Participants by Item and Condition

### Pilot 1 (Acceptability)

```{r}
df.full.tab.item.count <- df.query.acceptability %>%
  group_by(coordination, quantifier, combined_predicate) %>%
  count() %>%
  spread(quantifier, n)

df.full.tab.item.count %>% kable()

df.full.tab.item.count %>% 
  gather(quantifier, n, all, generic, most) %>%
  group_by(coordination) %>%
  summarize(n = sum(n)) %>% kable()
```

### Pilot 2 (Truth)

```{r}
df.full.tab.item.count <- df.query.truth %>%
  group_by(coordination, quantifier, combined_predicate) %>%
  count() %>%
  spread(quantifier, n)

df.full.tab.item.count %>% kable()

df.full.tab.item.count %>% 
  gather(quantifier, n, generic, most) %>%
  group_by(coordination) %>%
  summarize(n = sum(n)) %>% kable()
```

## Pilot 1 (Acceptability)

### Acceptability Judgements by Participant
 
Histogram of all of a single participant's acceptability judgements, collapsed across trials and color coded for the number of correct responses on the memory check.  
* fill = number of correct responses on the memory check (out of 10)  
* facet = participants  

```{r fig.height = 10}
df.query.acceptability %>%
  ggplot(., aes( x = response, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1)) +
  ylab("Number of Judgements") +
  xlab("Acceptability Rating")
```

### Histograms of Acceptability Judgements by Coordination and Quantifier (collapsed across item)

```{r fig.height = 8}
df.query.acceptability %>%
  ggplot(aes( x = response ))+
  geom_histogram()+
  facet_grid(coordination ~ quantifier) +
  xlab("Acceptability Rating") +
  ylab("Number of Trials")
```

### Pirate Plots by Coordination and Quantifier (collapsed across item)

```{r}
df.bs <- df.query.acceptability %>%
  group_by(quantifier, coordination) %>%
  tidyboot_mean(column = response)
  
ggplot(df.bs, aes( x = quantifier))+
  scale_fill_manual(values=c("#f4424e", "#4049f7", "#40f3f9")) +
  scale_color_manual(values=c("#f4424e", "#4049f7", "#40f3f9")) +
  geom_jitter(data = df.query.acceptability,
             inherit.aes = F, aes(x = quantifier, y = response, color = quantifier), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean, fill = quantifier),
           width = 0.8, alpha = 0.3, color = 'white')+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8),  size = 1.2, color = 'white')+  
  ylab("Acceptability Rating")+
  facet_wrap(~coordination)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  xlab("Quantifier")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "top")+
  guides(fill = F, color = F)
```

### Generic VP Analysis

```{r}
df.generic.vp <- df.query.acceptability %>%
  filter(quantifier == "generic", coordination == "vp") %>%
  mutate(response = response - 0.5)
generic.vp.model <- lmer(response ~ 1 + (1 | workerid) + (1 | combined_predicate),
                         data = df.generic.vp)
summary(generic.vp.model)
```

## Pilot 2 (Truth)

### Confidence Intervals by Coordination and Quantifier (collapsed across item)

```{r}
df_sample <- function(i) {
  df.query.truth %>% 
    group_by(quantifier, coordination) %>%
    sample_frac(replace = TRUE) %>%
    group_by(quantifier, coordination, response) %>%
    count() %>%
    group_by(quantifier, coordination) %>%
    mutate(prop = n/sum(n), sample = i) %>%
    filter(response == TRUE)
}
df_resampled <- map_df(1:10, df_sample)
df_ci <- df_resampled %>%
  group_by(coordination, quantifier) %>%
  summarise(mean = mean(prop), ci_lower = ci_lower(prop), ci_upper = ci_upper(prop))

ggplot(df_ci) +
  geom_col(aes(x = quantifier, y = mean, fill = quantifier), color='black') +
  geom_linerange(aes(x = quantifier, ymin = ci_lower, ymax = ci_upper)) +
  facet_grid(~ coordination) +
  scale_fill_viridis(discrete = TRUE, guide = FALSE) +
  ylab("Proportion of 'True' Responses") +
  xlab("Quantifier")
```

The model shows an interaction of quantifier and coordination level.

```{r}
contrasts(df.query.truth$coordination) <- contr.treatment
contrasts(df.query.truth$quantifier) <- contr.treatment
fit.truth <- brm(response ~ coordination * quantifier + (1 + coordination * quantifier | workerid) + (1 + coordination * quantifier | combined_predicate),
                  data = df.query.truth,
                  family = "bernoulli")
summary(fit.truth)
stanplot(fit.truth)
```

## By-item Analyses

### Pilot 1 (Acceptability)

#### Pirate Plots (by item)

```{r fig.width=13, fig.height = 30}
df.bs.item <- df.query.acceptability %>%
  group_by(coordination, quantifier, combined_predicate) %>%
  tidyboot_mean(column = response)

ggplot(df.bs.item, aes( x = quantifier, fill = quantifier))+
  scale_color_manual(values=c("#f4424e", "#4049f7", "#40f3f9")) +
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1, alpha = 0.5)+  
  geom_point(data = df.query.acceptability, 
             position = position_jitterdodge(),
             inherit.aes = F, aes(x = quantifier, y = response, color = quantifier), 
             alpha = 0.8)+
  ylab("Acceptability Rating")+
  facet_wrap(~combined_predicate + coordination, ncol = 4)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  xlab("")+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "top")
```

#### Confidence Intervals (by item)

```{r fig.height = 15}
ggplot(df.bs.item, aes(x = combined_predicate, color = quantifier)) +
  scale_color_manual(values=c("#f4424e", "#4049f7", "#40f3f9")) +
  geom_pointrange(aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                 position = position_dodge(0.6)) +
  facet_wrap(~coordination) +
  xlab("Item") +
  ylab("Acceptability Rating") +
  coord_flip()
```

#### Histograms of Acceptability Ratings by Item

##### by Coordination

```{r fig.height = 20}
df.query.acceptability %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_grid( combined_predicate ~coordination, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

##### by Quantifier

```{r fig.height = 20}
df.query.acceptability %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_grid( combined_predicate ~quantifier, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

### Pilot 2 (Truth)

#### Confidence Intervals (by item)

```{r fig.height = 15}
df_sample_item <- function(i) {
  df.query.truth %>% 
    group_by(combined_predicate, quantifier, coordination) %>%
    sample_frac(replace = TRUE) %>%
    group_by(combined_predicate, quantifier, coordination, response) %>%
    count() %>%
    group_by(combined_predicate, quantifier, coordination) %>%
    mutate(prop = n/sum(n), sample = i) %>%
    filter(response == TRUE)
}
df_resampled_item <- map_df(1:1000, df_sample_item)
df_ci_item <- df_resampled_item %>%
  group_by(combined_predicate, coordination, quantifier) %>%
  summarise(mean = mean(prop), ci_lower = ci_lower(prop), ci_upper = ci_upper(prop))

ggplot(df_ci_item, aes(x = combined_predicate, color = quantifier)) +
  scale_color_manual(values=c("#f4424e", "#4049f7")) +
  geom_pointrange(aes(y = mean, ymin = ci_lower, ymax = ci_upper),
                 position = position_dodge(0.6)) +
  facet_wrap(~coordination) +
  xlab("Item") +
  ylab("Proportion of True Responses") +
  coord_flip()
```
