---
title: "Quantifiers under VP-Coordination"
author: "Karen Gu"
date: "2/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(viridis)
library(tidyboot)
theme_set(theme_few())
```

## Number of Participants by Item and Condition

```{r}
df.query <- read.csv('./preprocessing/elephants-quantifier-vp-20190221.csv')
df.full.tab.item.count <-  df.query %>% filter(condition ==  "uninterrupted", trial_type == "critical") %>%
  group_by(quantifier, predicate_1) %>%
  count() %>%
  spread(quantifier, n) 

df.full.tab.item.count %>% kable()

df.full.tab.item.count %>% 
  gather(quantifier, n, all, generic, most) %>%
  group_by(quantifier) %>%
  summarize(n = sum(n)) %>% kable()
```

## Filler Trials

These used quantifiers (and thus we have strong idea about literal meaning).

```{r}
df.query.filler <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num, 
         rt, trial_type, quantifier, page_type, key, val)

df.query.filler  %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_wrap(~quantifier + condition)
```

## Critical Trials (collapsed across item)

### Histograms of Prevalence Estimates by Condition and Quantifier (collapsed across item)

```{r fig.height = 10}
df.query.critical <- df.query %>%
  filter(!memory_fail, !slider_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         quantifier,
         trial_type, predicate_1, predicate_2, 
         key, val, page_type, memory_fail, slider_fail) %>%
  filter(trial_type == "critical") %>%
  rowwise() %>%
  mutate(condition = factor(condition, 
                            levels = c("interrupted", 
                                       "uninterrupted",
                                       "nme_interrupted",
                                       "nme_uninterrupted"),
                            labels = c('"...live in Africa __"\nQ2(Asia)',
                                       '"...live in Africa and Asia"\nQ2(Asia)',
                                       '"...live in Africa __"\nQ2(bugs)',
                                       '"...live in Africa and eat bugs"\nQ2(bugs)')),
         key = factor(key, levels = c("response_1", "response_2"),
                      labels = c("% live in Africa", "% property 2")))

df.query.critical %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid(quantifier + condition ~ key)
```

### Pirate Plots by Condition and Quantifier (collapsed across item)

```{r}
df.bs.query.critical <- df.query.critical %>%
  group_by(quantifier, condition, key) %>%
  tidyboot_mean(column = val)
  
ggplot(df.bs.query.critical, aes( x = condition, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(data = df.query.critical, position = position_jitterdodge(),
             inherit.aes = F, aes(x = condition, y = val, color = key), 
             alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), 
                position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  ylab("Implied prevalence rating")+
  facet_wrap(~quantifier)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "top")
```

### Histograms of Prevalence Estimates by Quantifier for Condition 2 (collapsed across item)

```{r}
df.query.critical %>%
  filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)") %>%
  ggplot(., aes( x = val ))+
  geom_histogram()+
  facet_grid( quantifier~ key, scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

## By-item Analyses

### Number of Participants by Item and Quantifier

```{r}
df.tab.item.count <-  df.query.critical %>% filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)", str_detect(key, "Africa")) %>%
  group_by(quantifier, predicate_1) %>%
  count() %>%
  spread(quantifier, n) 

df.tab.item.count %>% kable()

df.tab.item.count %>% 
  gather(quantifier, n, all, generic, most) %>%
  group_by(quantifier) %>%
  summarize(n = sum(n)) %>% kable()
```

### Comparison of Prevalence Estimates for "(all/most/gen) elephants live in Africa and live in Asia"

```{r fig.width=13, fig.height = 10}
df.bs.cond2.item <- df.query.critical %>%
  filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)") %>%
  group_by(quantifier, condition, predicate_1, key) %>%
  tidyboot_mean(column = val)


ggplot(df.bs.cond2.item, aes( x = key, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_point(data = df.query.critical %>% filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)"), 
             inherit.aes = F, aes(x = key, y = val, color = key), 
             alpha = 0.8)+
  geom_line(data = df.query.critical %>% filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)"), 
            position = position_dodge(),
             inherit.aes = F, aes(x = key, y = val, group = workerid), 
             alpha = 0.6)+
  ylab("Implied prevalence rating")+
  facet_grid(quantifier~predicate_1)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "top")
```

```{r}
ggplot(df.bs.cond2.item, aes( x = quantifier, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
    geom_col(position = position_dodge(0.8),
           aes(y = mean),
           width = 0.8, alpha = 0.3, color = 'black')+
  geom_point(data = df.query.critical %>% filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)"), 
             position = position_jitterdodge(),
             inherit.aes = F, aes(x = quantifier, y = val, color = key), 
             alpha = 0.8)+
  ylab("Implied prevalence rating")+
  facet_wrap(~predicate_1, nrow = 2)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "top")
```

### Histograms of Prevalence Estimates by Item

#### % live in Africa

```{r fig.height = 10}
df.query.critical %>%
  filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)",
         key == "% live in Africa") %>%
  ggplot(., aes( x = val ))+
  xlab("% live in Africa") +
  geom_histogram()+
  facet_grid( predicate_1 ~condition+ quantifier , scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```

#### % live in Asia

```{r fig.height = 10}
df.query.critical %>%
  filter(condition ==  "\"...live in Africa and Asia\"\nQ2(Asia)",
         key == "% property 2") %>%
  ggplot(., aes( x = val ))+
  xlab("% property 2") + 
  geom_histogram()+
  facet_grid( predicate_2 ~condition+ quantifier , scales = 'free')+
  theme(strip.text.y = element_text(angle = 0))
```
