---
title: "elephants-2-pilot"
author: "MH Tessler"
date: "1/17/2019"
output: github_document
---

[Link to experiment](http://www.mit.edu/~tessler/projects/elephants/experiments/elephants-2.html)

Participants read a storybook about an alien planet. Each chapter consists of some description of a kind, for example, elephants. The participants are either asked in the middle of a chapter or at the end of the chapter what percentage of the kind they think a particular predicate applies to (for instance, what percentage of elephants do you think live in Africa?).
#### Changes from Pilot 1
- added practice trial at the beginning

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(tidyverse)
library(knitr)
library(ggthemes)
library(viridis)
library(tidyboot)
library(ggpirate)
theme_set(theme_few())
data.path <- "../data/elephants-2/elephants-2"
```

## Subject information

```{r}
df.subj <- read_csv(
  paste(data.path, "-subject_information.csv", sep = "")
  ) %>%
  mutate(language = gsub("\"", "", language),
         enjoyment = gsub("\"", "", enjoyment),
         age = gsub("\"", "", age),
         gender = gsub("\"", "", gender),
         problems = gsub("\"", "", problems),
         comments = gsub("\"", "", comments))

df.subj %>%
  select(workerid, language, enjoyment, age, gender, problems, comments) %>%
  kable(.)
```

## Attention check 

### Slider practice

Before the experiment, participants practiced using the sliders to rate the prevalence (x) of 3 category-property pairs:

- dogs bark (coded as correct if x > 0.5)
- birds are male (coded as correct if 0.25 < x < 0.75)
- ticks carry lyme disease (coded as correct if x < 0.50)

Several (9) participants rated % of ticks with Lyme disease as > 50% (but got other two slider questions correct). Not excluding anyone using this metric.

### Memory check

After the story, participants select statements they recall learning from a list of 10 generic statements about novel animals (5 true, 5 distractor). They are also asked to explain what they did in the experiment.


```{r}
df.attn <- read_csv(
  paste(data.path, "-catch_trials.csv", sep = "")
  ) %>%
  mutate(property = gsub("\"", "", property),
         condition = gsub("\"", "", condition))

# slider bar check

workers.fail.sliders <- df.attn %>% 
  filter(condition == "practice") %>%
  mutate(correct = case_when(
    property == "dogs bark" ~ response > 0.5,
    property == "birds are male" ~ response > 0.25 && response < 0.75,
    property == "ticks carry lyme disease" ~ response < 0.5
  )) %>%
  group_by(workerid) %>% 
  summarize(not_all_correct = sum(correct) < 3,
            not_two_correct = sum(correct) < 2) %>%
  filter(not_two_correct) %>%
  pull(workerid)

# memory check data
df.mmry <- df.attn %>%
  filter(condition == "memory_check") %>%
  mutate(correct = as.numeric(correct)) %>%
  #filter(correct != -1) %>% # remove explanations
  group_by(workerid, tested_on) %>%
  summarize(n_correct = sum(correct)) %>%
  ungroup() %>%
  spread(tested_on, n_correct) %>%
  rename(correct_rejections = `0`, 
         hits = `1`) %>%
  mutate(n_correct = correct_rejections + hits) 

workers.fail.memory <- df.mmry %>% filter(n_correct < 7) %>% pull(workerid)

ggplot(df.mmry, aes( x = n_correct ))+
  geom_bar()+
  xlab("n correctly recognized (or correctly rejected)")+
  scale_x_continuous(limits = c(0, 10.5), breaks = c(0, 4, 5, 6, 7, 8, 9, 10))+
  ylab("n participants")

df.mmry %>%
  kable(.)
```

### Explanations of task

```{r}
df.expln <- df.attn %>%
  filter(correct == -1) 

df.expln %>%
  select(workerid, property) %>%
  rename(explanation = property) %>%
  kable(.)
```

```{r}
df.trials <- left_join(
    read_csv(
    paste(data.path, "-trials.csv", sep = "")
    ) %>% 
    mutate(
      page_type = gsub("\"", "", page_type),
      trial_type = gsub("\"", "", trial_type),
      kind = gsub("\"", "", kind),
      #generic = gsub("\"", "", generic),
      page_content = gsub("\"", "", page_content),
      predicate_1 = gsub("\"", "", predicate_1),
      predicate_2 = gsub("\"", "", predicate_2),
      #verb = gsub("\"", "", verb),
      chapter = gsub("\"", "", chapter),
      condition = gsub("\"", "", condition),
      memory_fail = workerid %in% workers.fail.memory
      ),
    df.mmry %>% select(workerid, n_correct)
)

df.query <- df.trials %>%
  filter(page_type == "query")
```

## Prevalence Estimates per Participant
 
Histogram of all of a single participant's prevalence estimates, collapsed across trials and color coded for the number of correct responses on the memory check.
- fill = number of correct responses on the memory check (out of 10)
- facet = participants

```{r}
df.query  %>%
  ggplot(., aes( x = response, fill = n_correct ))+
  geom_histogram()+
  facet_wrap(~workerid)+
  scale_fill_viridis()+
  scale_x_continuous(breaks = c(0, 0.5, 1))
```

## Filler Trials

For all subsequent analyses, we will only consider participants who answered 7 or more items correctly in the statement identification task. (n = `r df.mmry %>% filter(n_correct >= 7) %>% nrow() ` out of `r nrow(df.mmry)`)

these used quantifiers (and thus we have strong idea about literal meaning)

- "no Xs are poisonous to lorches"
- "some build permanent structures"
- "all have hollow bones"
- "all aliens love Zorxon"
- "no storms (or few) on Dax result in permanent damage..."

```{r}
df.query.filler <- df.query %>%
  filter(!memory_fail) %>%
  filter(trial_type == "filler") %>%
  select(workerid, condition, chapter_num, rt, trial_type, predicate_1, page_type, response)

df.query.filler  %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_wrap(~predicate_1 + condition)
```

## Critical Trials (collapsed across item)

```{r}
df.query.critical <- df.query %>%
  filter(!memory_fail) %>%
  select(workerid, condition, chapter_num, rt, 
         trial_type, predicate_1, page_type, response, memory_fail) %>%
  filter(trial_type == "critical") %>%  
  mutate(condition = factor(condition, levels = c("uninterrupted_irrelevant", "uninterrupted"),
                            labels = c("..Africa", "..Africa and Asia")))

df.query.critical %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  facet_wrap(~condition)
```

### bootstrapped 95% confidence intervals (collapsed across items)

```{r fig.width = 4, fig.height = 3}
df.bs.query.critical <- df.query.critical %>%
  group_by(condition) %>%
  tidyboot_mean(column = response)

df.bs.query.critical %>%
  ggplot(., aes( x = "manipulation", fill = condition, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()
```

## Number of Trials by Stimulus and Condition

```{r}
df.query.critical %>%
  filter(!memory_fail) %>%
  ungroup() %>%
  group_by(condition, predicate_1) %>%
  count() %>%
  spread(condition, n) %>% kable()
```

## Critical Trials (by Item)
### Pirate plots by Item

```{r}
df.query.critical %>%
  filter(!memory_fail) %>%
  ggplot(., aes( x = condition, fill = condition, y = response))+
  geom_pirate(aes(color = condition, fill = condition),
              violins = F)+
  #geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  facet_wrap(~predicate_1, nrow = 2)+
  ylab("% Africa")+
  #geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  scale_color_solarized()+
  scale_y_continuous(breaks = c(0, 0.5, 1))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
```

### 95% CIs by Item

```{r}
df.bs.crit.item <- df.query.critical %>%
  filter(!memory_fail) %>%
  group_by(condition, predicate_1) %>%
  tidyboot_mean(column = response)

df.bs.crit.item %>%
  ggplot(., aes( x = predicate_1, fill = condition, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))+
  xlab("item")
```

## First Trial
"Krens ascribe to the Caboo religion...and the Daith religion."
```{r}
df.query.critical %>%
  group_by(workerid, condition) %>%
  mutate(first_trial  = min(chapter_num),
         is_first = chapter_num == first_trial) %>%
  filter(is_first) %>%
  ggplot(., aes( x = response ))+
  geom_histogram()+
  xlim(0, 1)+
  facet_wrap(~condition)
```

```{r}
df.query.critical %>%
  group_by(workerid, condition) %>%
  mutate(first_trial  = min(chapter_num),
         is_first = chapter_num == first_trial) %>%
  filter(is_first) %>%
  group_by(condition) %>%
  tidyboot_mean(column = response) %>%
  ggplot(., aes( x = "manipulation", fill = condition, y = mean, ymin = ci_lower, ymax = ci_upper ))+
  geom_col(position = position_dodge(0.8), width = 0.8, alpha = 0.8, color = 'black')+
  ylab("% Africa")+
  geom_errorbar(position = position_dodge(0.8), width = 0.3)+
  scale_fill_solarized()
```

