---
title: "Conjunctive generics simulations"
author: "MH Tessler"
date: "1/19/2019"
output: github_document
---


```{r}
library(rwebppl)
library(tidyverse)
library(ggthemes)
library(viridis)
library(cowplot)
theme_set(theme_few())
```

Here we explore the behavior of variants of an RSA model that can interpret conjunctive generic sentences such as "Elephants live in Africa and Asia". 
For the simple model variants, the first assumption is that the sentence is parsed as "Elephants live in Africa. Elephants live in Asia."

### Model variants

#### Prior specifications

The important assumption about the prior is that the properties "living in Africa" and  "living in Asia" are (probably) mutually exclusive. One way to cash this out is to impose a constraint on the two prevalence levels: The sum of the % that live in Africa and the % that live in Asia should probably not exceed 100%. 

Otherwise, we assume the marginal distributions on Africa and Asia are symmetric, and either:

1. Uniform(0, 1)
2. Multimodal with peaks at 0%, 25%, 50%, 75%, 100%

The latter version of the prior will probably match participants' slider bar behavior better.

#### Interpretation models

1. Literal listener
2. "Unlifted threshold" pragmatic listener
3. "Lifted threshold" pragmatic listener

For the pragmatic models, there is a choice of the alternative utterances considered by the speaker. Here, we test two sets of alternatives:

A. ["Elephants live in X", silence] where X will be either Africa or Asia depending on the sentence heard.
B. ["Elephants live in Africa", "Elephants live in Asia", "silence"]

The set where "Elephants live in Africa and Asia" is an alternative is also a possiblity, though with the simple version of the model, we make the strong assumption that the properties are parsed independently (i.e., you run the listener model twice: Once for Africa, once for Asia) so it is a little more complex to keep the conjunctive generic as an alternative (as it requires running the models, twice, etc..)


## Literal Listener 

L0 is run for each prior (uniform and multimodal)

```{r}
priorParameters <- list(
  multimodal = list(
    c1 = data.frame(a = 1 , b = 100),
    #c2 = data.frame(a = 15, b = 15),
    #c3 = data.frame(a = 15, b = 45),
    c4 = data.frame(a = 25, b = 1)
    ),
  # multimodal2 = list(
  #   c1 = data.frame(a = 1 , b = 100), 
  #   #c4 = data.frame(a = 1 , b = 100), 
  #   c2 = data.frame(a = 30, b = 30), 
  #   #c3 = data.frame(a = 15, b = 45), 
  #   c3 = data.frame(a = 50, b = 1),
  #   c5 = data.frame(a = 50, b = 1)
  #   ),
  # multimodal3 = list(
  #   c1 = data.frame(a = 1 , b = 100), 
  #   #c4 = data.frame(a = 1 , b = 100),
  #   c2 = data.frame(a = 30, b = 30), 
  #   #c3 = data.frame(a = 15, b = 45), 
  #   c3 = data.frame(a = 50, b = 1),
  #   #c5 = data.frame(a = 50, b = 1)
  #   ),
  # u_shaped = list(
  #   c1 = data.frame(a = 0.1, b = 1)# 
  #   #@c3 = data.frame(a = 1, b = 1)
  #   ),
  uniform = list(c1 = data.frame(a = 1 , b = 1))
)

rs.l0.eleph <- data.frame()
for (correlatedPriors in c(T, F)){
  for (priorName in names(priorParameters)){
  
  rs.eleph <- webppl(program_file = "elephants-L0.wppl",
                   data = list(correlatedPrior = correlatedPriors, params = priorParameters[[priorName]]), 
                   data_var = "priorInfo")
  
  rs.l0.eleph <- bind_rows(
    rs.l0.eleph, 
    bind_rows(
      as.data.frame(rs.eleph$JointPrevalencePrior) %>%
        mutate(src = "prior"),
      as.data.frame(rs.eleph$africaStatePosterior) %>%
        mutate(src = "AF"),
      as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior) %>%
        mutate(src = "AFAS")
    ) %>% rename(prob = probs, 
               africa = support.africa,
               asia = support.asia) %>% 
      mutate(priorName = priorName,
             correlatedPriors = correlatedPriors)
  )
  
  print(priorName)
  }
}

rs.l0.samp <- get_samples(rs.l0.eleph, 50000) %>%
  mutate(src = factor(src, levels = c("prior", "AF", "AFAS")))
```

### Uniform priors 

#### Joint distributions

Shown left to Right: Prior disribution on prevalence for living in Africa and Asia; Posterior upon living "Elephants live in Africa", Posterior upon then hearing "Elephants live in Asia" (after already hearing they live in Africa)

```{r}
rs.l0.samp %>% 
  filter(priorName == "uniform") %>%
    mutate(correlatedPriors = factor(correlatedPriors, levels = c(T, F),
                                   labels = c("correlated\npriors", "uncorrelated\npriors")),
         priorName = factor(priorName, levels = c("uniform", "multimodal", "multimodal2", "multimodal3", "bimodal"),
                      labels = c("Uniform", "Multimodal v1", "Multimodal v2", "multimodal3", "bimodal")),
         src = factor(src, levels = c("prior", "AF", "AFAS"),
                      labels = c("Prior", "...live in Africa",
                                 "...and Asia"))) %>%
ggplot(., aes(x = asia, y = africa))+
  #geom_bin2d(bins = 10)+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  theme_black()+
  scale_fill_viridis(option = "plasma")+
  facet_grid(correlatedPriors~src)+
  xlab("% lives in Asia")+
  ylab("% lives in Africa")+
  guides(fill = guide_legend(title = "Probability density", reverse = T),
         color = guide_legend(title = "Question"))+
  theme(strip.text.y = element_text(angle = 0))+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 1))+
  coord_fixed()

#ggsave("~/projects/elephants/writing/cogsci2019/figs/model_joint.pdf", width = 8, height = 4)

ggsave("~/Documents/talks/coglunch-0319/figs/elephants-models.pdf", width = 6, height = 3.5)

```

#### Marginal distributions


```{r}
rs.l0.samp.rf <- rs.l0.samp %>%
  gather(key, val, -src, -priorName, -correlatedPriors) %>%
  mutate(correlatedPriors = factor(correlatedPriors, levels = c(T, F),
                                   labels = c("correlated priors", "uncorrelated priors")),
         key = factor(key, levels = c("africa", "asia"),
                      labels = c("% live in Africa", "% live in Asia")),
         # priorName = factor(priorName, levels = c("uniform", "multimodal", "multimodal2", "multimodal3", "bimodal"),
         #              labels = c("Uniform", "Multimodal v1", "Multimodal v2", "multimodal3", "bimodal")),
         priorName = factor(priorName, levels = c("uniform",  #"u_shaped", 
                                                  "multimodal"),
                      labels = c("Uniform", #"U-shaped", 
                                 "Multimodal")),
         src = factor(src, levels = c("prior", "AF", "AFAS"),
                      labels = c("Prior", "...live in Africa",
                                 "...live in Africa and Asia")))



rs.l0.samp.rf.mean <- rs.l0.samp.rf %>%
  group_by(src, key, correlatedPriors, priorName) %>%
  summarize(expval = mean(val))
  #filter(priorName == "uniform", correlatedPriors == T) %>%

ggplot(rs.l0.samp.rf,# %>% filter(priorName %in% c("Multimodal")),
       aes( x = src, y = val , fill = key))+
  #facet_wrap(~src)+
  geom_violin(adjust = 3.5, alpha = 0.3, color = 'black')+
  geom_point(data = rs.l0.samp.rf.mean,# %>% filter(priorName %in% c("Multimodal")),# %>%
         #filter(priorName %in% c("Uniform", "Multimodal v1")),
         inherit.aes = T,
                 aes( x = src, group = key, y = expval, fill = key),
             position = position_dodge(width = 0.9),
             shape = 23, size = 3, stroke = 2)+
  facet_grid(priorName~correlatedPriors, scales = 'free')+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.text.y = element_text(angle = 0),
        legend.position = "bottom")

ggsave("~/projects/elephants/writing/cogsci2019/figs/model_2.pdf", width = 8, height = 6)
```



```{r}
rs.l0.samp.rf.inc <- rs.l0.samp.rf %>% filter(
  priorName == "Multimodal", correlatedPriors == "correlated priors",
  src %in% c("...live in Africa", "...live in Africa and Asia")
)

rs.l0.samp.rf.inc2<- bind_rows(
  bind_rows(
    rs.l0.samp.rf.inc %>% mutate(m = "Strong incremental"),
    rs.l0.samp.rf.inc %>% mutate(src = "...live in Africa and __",
                                 m = 'Strong incremental')
  ),
  bind_rows(
    rs.l0.samp.rf.inc %>% mutate(m = "Weak incremental"),
    rs.l0.samp.rf.inc %>% filter(src == "...live in Africa") %>%
      mutate(src = "...live in Africa and __",
                                 m = 'Weak incremental')
  )
)
  

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

rs.l0.samp.rf.inc2 %>%
  group_by(priorName, src, correlatedPriors, key, m) %>%
  summarize(expval = mean(val)) %>%
  ungroup() %>%
  mutate(src = factor(src, levels = c("...live in Africa", "...live in Africa and __", "...live in Africa and Asia"),
                             labels = c("...live in Africa     ", "and", "Asia"))) %>%
  ggplot(., aes( x = src, y = expval, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5, color = 'white')+
  geom_col(position = position_dodge(0.8),
           width = 0.8, #alpha = 0.3, 
           size = 0.75, color = 'white')+
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                #position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  ylab("Implied prevalence rating")+
  theme_black()+
  facet_wrap(~m)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  # scale_fill_solarized()+
  # scale_color_solarized()+
    scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust = 0.5),
        axis.ticks.x = element_blank(),
        legend.position = "bottom")

#ggsave("~/projects/elephants/writing/cogsci2019/figs/incremental.pdf", width = 5, height = 3.5)

ggsave("~/Documents/talks/coglunch-0319/figs/elephants-models-incremental-expval.pdf", 
       width = 5, height = 3.5)

```

```{r}
#rs.l0.samp.rf.inc2 %>%
rs.l0.samp.rf.mean %>%
  filter(src %in% c("...live in Africa",  "...live in Africa and Asia"),
         priorName == "Multimodal") %>%
  # group_by(priorName, src, correlatedPriors, key, m) %>%
  # summarize(expval = mean(val)) %>%
  ungroup() %>%
  mutate(src = factor(src, levels = c("...live in Africa",  "...live in Africa and Asia"),
                             labels = c("...live in Africa     ",  "and Asia"))) %>%
  ggplot(., aes( x = src, y = expval, fill = key))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = 0.5)+
  geom_col(position = position_dodge(0.8),
           width = 0.8, #alpha = 0.3, 
           size = 0.75, color = 'white')+
  #geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), 
                #position = position_dodge(0.8), width = 0.3, size = 1.2)+  
  ylab("Implied prevalence rating")+
  theme_black()+
  facet_wrap(~correlatedPriors)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  # scale_fill_solarized()+
  # scale_color_solarized()+
    scale_fill_manual(values = c("#268bd2", "#859900"))+
  scale_color_manual(values = c("#268bd2", "#859900"))+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 0, vjust = 1, hjust = 0.5),
        axis.ticks.x = element_blank(),
        legend.position = "bottom")

ggsave("~/Documents/talks/coglunch-0319/figs/elephants-models-expval.pdf", 
       width = 5, height = 3.5)

```


```{r}
library(ggridges)
ggplot(rs.l0.samp.rf %>% filter(priorName %in% c("Multimodal")),
       aes( x = val, y = src , fill = key))+
  #facet_wrap(~src)+
  geom_violin(adjust = 1, alpha = 0.3, color = 'black')+
  geom_density_ridges(position = position_dodge())+
  # geom_point(data = rs.l0.samp.rf.mean %>% filter(priorName %in% c("Multimodal")),# %>%
  #        #filter(priorName %in% c("Uniform", "Multimodal v1")),
  #        inherit.aes = T,
  #                aes( x = src, group = key, y = expval, fill = key),
  #            position = position_dodge(width = 0.9),
  #            shape = 23, size = 3, stroke = 2)+
  facet_grid(priorName~correlatedPriors, scales = 'free')+
  ylab("Implied prevalence rating")+
  #scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.text.y = element_text(angle = 0),
        legend.position = "bottom")+
  coord_flip()

```

```{r}
rs.l0.samp %>%
  #filter(priorName == "uniform") %>%
  gather(key, val, -src, -priorName, -correlatedPriors) %>%
ggplot(., aes(x = val, color = key))+
  geom_density(adjust = 2.5, fill = 'white', alpha = 0.3,
               position = position_dodge(width = 0.05))+
  facet_grid(correlatedPriors+priorName~src, scales = 'free')+
  scale_color_solarized()+
  xlab("marginal prevalence")+
  ylab("scaled probability density")+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))
```

### Multimodal priors 

```{r}
ggplot(rs.l0.samp %>%
         filter(priorName == "multimodal"), aes(x = asia, y = africa))+
  #geom_bin2d(bins = 10)+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  scale_fill_viridis()+
  facet_grid(.~src)+
  xlab("% lives in Asia")+
  ylab("% lives in Africa")
```

```{r}
rs.l0.samp %>%
  filter(priorName == "multimodal") %>%
  gather(key, val, -src, -priorName) %>%
ggplot(., aes(x = val))+
  #geom_bin2d(bins = 10)+
  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_grid(key~src)+
  xlab("marginal prevalence")+
  ylab("scaled probability density")
```

## Pragmatic Listener (lifted threshold)

L1 is run for each prior (uniform and multimodal), both sets of alternatives (just silence, alternative property + silence), a few settings of rationality and cost

```{r}
priorParameters <- list(
  multimodal = list(
    c1 = data.frame(a = 45 , b = 15), 
    c2 = data.frame(a = 30, b = 30), 
    c3 = data.frame(a = 15, b = 45), 
    c4 = data.frame(a = 50, b = 1)
    ),
  uniform = list(c1 = data.frame(a = 1 , b = 1))
)

rs.l0.eleph <- data.frame()
for (priorName in names(priorParameters)){
  
  rs.eleph <- webppl(program_file = "elephants-L0.wppl",
                   data = priorParameters[[priorName]], 
                   data_var = "priorParameters")
  
  rs.l0.eleph <- bind_rows(
    rs.l0.eleph, 
    bind_rows(
      as.data.frame(rs.eleph$JointPrevalencePrior) %>%
        mutate(src = "prior"),
      as.data.frame(rs.eleph$africaStatePosterior) %>%
        mutate(src = "AF"),
      as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior) %>%
        mutate(src = "AFAS")
    ) %>% rename(prob = probs, 
               africa = support.africa,
               asia = support.asia) %>% 
      mutate(priorName = priorName)
  )
  
  print(priorName)
}

rs.l0.samp <- get_samples(rs.l0.eleph, 50000) %>%
  mutate(src = factor(src, levels = c("prior", "AF", "AFAS")))
```


```{r}
timestamp()
rs.eleph <- webppl(program_file = "elephants-L1.wppl")
timestamp()
#rs.eleph
```

```{r}
rs.l1.africa <- as.data.frame(rs.eleph$africaStatePosterior)
rs.l1.asiaafrica <- as.data.frame(rs.eleph$AfricaAndAsiaStatePosterior)
rs.l1.asiaafrica.prior <- as.data.frame(rs.eleph$JointPrevalencePrior)

rs.l1.prior.samp <- get_samples(rs.l1.asiaafrica.prior %>%
                               rename(prob = probs), 50000)
```
### Joint distributions

#### Prior

```{r}
ggplot(rs.l1.prior.samp, aes(x = support.africa, y = support.asia))+
  #geom_bin2d(bins = 10)+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  scale_fill_viridis()+
  xlab("% lives in Africa")+
  ylab("% lives in Asia")
```


#### "Elephants live in Africa"

```{r}
rs.l1.africa.samp <- get_samples(rs.l1.africa %>% rename(prob = probs), 50000)

ggplot(rs.l1.africa.samp, aes(x = support.africa, y = support.asia))+
  #geom_bin2d(bins = 10)+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  scale_fill_viridis()+
  xlab("% lives in Africa")+
  ylab("% lives in Asia")
```

#### "Elephants live in Africa and Asia"

```{r}
rs.l1.africa.asia.samp <- get_samples(rs.l1.asiaafrica %>% rename(prob = probs), 50000)

ggplot(rs.l1.africa.asia.samp, aes(x = support.africa, y = support.asia))+
  #geom_bin2d(bins = 10)+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  scale_fill_viridis()+
  xlab("% lives in Africa")+
  ylab("% lives in Asia")
```

##### marginals

```{r}

# save(rs.asia.marignals, rs.asiaafrica.marignals,rs.asiaafrica.priors,
#      file = "../paper/cached_results/modelSims-elephants.RData")
# 

rs.l1.asiaafrica.priors <- bind_rows(
  rs.l1.asiaafrica.prior %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.l1.asiaafrica.prior %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)


rs.l1.africa.marignals <- bind_rows(
  rs.l1.africa %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa"),
  rs.l1.africa %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia")
)

rs.l1.asiaafrica.marignals <- bind_rows(
  rs.l1.asiaafrica %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.l1.asiaafrica %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)

fig.eleph.0 <- get_samples(rs.l1.asiaafrica.priors, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 2, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('prevalence priors')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")

fig.eleph.1 <- get_samples(rs.l1.africa.marignals, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('"Elephants live in Africa..."')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("Prevalence")+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

fig.eleph.2 <- get_samples(rs.l1.asiaafrica.marignals, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("")+
  ggtitle('"...and Asia"')+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

cowplot::plot_grid(
  fig.eleph.0,
  fig.eleph.1,
  fig.eleph.2,
  nrow = 1,
  rel_widths =c(1,1, 1),
  labels = c("A", "B","C")
)
```


#### Africa

```{r}
ggplot(rs.asia.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)

```

#### Africa and Asia


```{r}

ggplot(rs.asiaafrica.marignals, aes(x = state, y = prob))+
  geom_col(position = position_dodge())+
  facet_wrap(~marginal)


rs.asiaafrica.priors <- bind_rows(
  rs.asiaafrica.prior %>%
    rename(state = support.asia) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "asia"),
  rs.asiaafrica.prior %>%
    rename(state = support.africa) %>%
    group_by(state) %>%
    summarize(prob = sum(probs)) %>%
    mutate(marginal = "africa")
)
```




#### Prior

```{r}
get_samples(rs.asiaafrica.priors, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 2, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('prevalence priors')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")
```
