---
title: "model v2"
author: "Karen Gu"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10)
library(rwebppl)
library(tidyverse)
library(ggthemes)
library(viridis)
library(cowplot)
library(tidyboot)
library(hBayesDM)
library(bayestestR)
theme_set(theme_few())
```

Here we explore the behavior of variants of an RSA model that can interpret conjunctive generic sentences such as "Elephants live in Africa and Asia". The model returns a joint distribution over four variables: the prevalence of elephants living in Africa (or both), the prevalence of elephants living in Asia (or both), the prevalence of elephants living in both, and the mutual exclusivity of the predicate "living in some continent", which is a binary variable.

## Prior specifications

We assume the marginal distributions on Africa and Asia are symmetric, and either:

1. Uniform(0, 1)
2. Multimodal with peaks at 0%, 50%, 100%
3. U-shaped

```{r}
priorParameters <- list(
  multimodal = list(
    c1 = data.frame(a = 1 , b = 100),
    c2 = data.frame(a = 15, b = 15),
    c4 = data.frame(a = 25, b = 1)
    ),
  u_shaped = list(data.frame(a = 0.1, b = 1)),
  uniform = list(data.frame(a = 1 , b = 1))
)
```

We also explore the effect of the belief in mutual exclusivity:

```{r}
meParams <- (1:10)/10
```

## Literal Listener - Effect of Prior Shape

We first explore the effect of the prior shape (uniform, multimodal, or u-shaped) on the literal listener. For all the analyses in this section, the prior probability of mutual exclusivity is .99.

```{r}
rs.l0.eleph <- data.frame()

for (priorName in names(priorParameters)){
  
  rs.eleph <- webppl(program_file = "elephants.wppl",
                   data = list(params = priorParameters[[priorName]], meProb = .99), 
                   data_var = "priorInfo")
  
  rs.l0.eleph <- bind_rows(
    rs.l0.eleph, 
    bind_rows(
      as.data.frame(rs.eleph$ambiguous_complete) %>%
        mutate(src = "ambiguous_complete"),
      as.data.frame(rs.eleph$cont1_complete) %>%
        mutate(src = "cont1_complete"),
      as.data.frame(rs.eleph$cont2_complete) %>%
        mutate(src = "cont2_complete"),
      as.data.frame(rs.eleph$prior) %>%
        mutate(src = "prior"),
      as.data.frame(rs.eleph$prefix) %>%
        mutate(src = "prefix"),
      as.data.frame(rs.eleph$full) %>%
        mutate(src = "full"),
      as.data.frame(rs.eleph$partial) %>%
        mutate(src = "partial")
    ) %>% rename(prob = probs, 
               africa = support.africa,
               asia = support.asia,
               both = support.both,
               me = support.me) %>% 
      mutate(priorName = priorName)
  )
}

rs.l0.samp <- get_samples(rs.l0.eleph, 50000) %>% 
  mutate(
    priorName = factor(
      priorName, 
      levels = c("uniform", "multimodal", "u_shaped", "bimodal"),
      labels = c("Uniform", "Multimodal", "U-shaped", "bimodal")
    ),
    src = factor(
      src, 
      levels = c(
        "prior", "ambiguous_complete", "cont1_complete", "cont2_complete", "prefix", "partial", "full"
      ),
      labels = c(
        "Prior",
        "Ambiguous Complete", 
        "And > Gen", 
        "Gen > And", 
        "Elephants live in Africa.", 
        "Elephants live in Africa and...", 
        "Elephants live in Africa and Asia."
      )
    )
  )
```

### Elephants live in Africa and Asia.

We report model predictions for the full conjunctive generic sentence. According to our grammar, this can be either: 

1. scoped such that gen > and
2. scoped such that gen < and
3. ambiguous such that the scope of gen vs. and is not known

#### Joint distributions

Here we show joint distributions over two variables:
1. living in Africa (or both)
2. living in Asia (or both)
for the three different choices of prior shape described above.

```{r}
complete.dists <-  c("Prior", "Ambiguous Complete", "And > Gen", "Gen > And")

plot_joint <- function(dist, name, cutoffs) {
  dist %>% 
  filter(priorName == name) %>%
ggplot(., aes(x = africa, y = asia))+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  scale_fill_viridis(option = "plasma")+
  xlab("% Africa")+
  ylab("% Asia")+
  facet_wrap(~src, labeller = labeller(facet_category = label_wrap_gen(width = 16)))+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = 'bottom',
        panel.spacing.x=unit(3, "lines"),panel.spacing.y=unit(1, "lines"))+
  scale_x_continuous(limits = cutoffs, breaks = cutoffs)+
  scale_y_continuous(limits = cutoffs, breaks = cutoffs)+
  coord_fixed()
}
```

##### Uniform prior

```{r}
plot_joint(rs.l0.samp %>% filter(src %in% complete.dists), "Uniform", c(0,1))
```

##### U-shaped prior

```{r}
plot_joint(rs.l0.samp %>% filter(src %in% complete.dists), "U-shaped", c(0,1))
```

##### Multimodal prior

```{r}
plot_joint(rs.l0.samp %>% filter(src %in% complete.dists), "Multimodal", c(.9,1))
```

#### Marginal distributions

We show marginal distributions for two different variables:
1. living in Africa (or both)
2. living in Asia (or both)
for each of the different prior shapes (vertical facet).

```{r}
rs.l0.samp.mean.complete <- rs.l0.samp %>%
  filter(src %in% complete.dists) %>%
  gather("key", "val", asia:africa) %>%
  group_by(key, priorName) %>%
  summarise(mean = mean(val))

rs.l0.samp %>%
  filter(src %in% complete.dists) %>%
  gather("key", "val", asia:africa) %>%
ggplot(aes( x = key, y = val , fill = key))+
  geom_violin(adjust = 3.5, alpha = 0.3, color = 'black')+
  geom_point(data = rs.l0.samp.mean.complete,
         inherit.aes = T,
                 aes( x = key, y = mean, fill = key),
             position = position_dodge(width = 0.9),
             shape = 23, size = 3, stroke = 2)+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  facet_grid(priorName~src)+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.text.y = element_text(angle = 0),
        legend.position = "bottom")
```

### Elephants live in Africa and...

We report model predictions for incomplete sentences, with full sentences to provide context. In particular, we report predictions for the following sentences:
1. Elephants live in Africa. (complete)
2. Elephants live in Africa and... (incomplete)
3. Elephants live in Africa and Asia (complete, same as Ambiguous Complete condition above)

```{r}
rs.l0.samp.inc <- rs.l0.samp %>%
         filter(! src %in% complete.dists | src == "Prior") %>%
  gather("key", "val", asia:africa)
rs.l0.samp.mean.inc <- rs.l0.samp %>%
  filter(! src %in% complete.dists | src == "Prior") %>%
  gather("key", "val", asia:africa) %>%
  group_by(key, priorName, src) %>%
  summarise(mean = mean(val))
rs.l0.samp.map.inc <- rs.l0.samp %>%
  filter(! src %in% complete.dists | src == "Prior") %>%
  gather("key", "val", asia:africa) %>%
  group_by(key, priorName, src) %>%
  summarise(map = estimate_mode(val))
```


#### Joint distributions

##### Uniform prior

```{r}
plot_joint(rs.l0.samp %>% filter(! src %in% complete.dists), "Uniform", c(0, 1))
```


#### Marginal distributions

```{r}
rs.l0.inc.samp.mean <- rs.l0.samp %>%
  filter(! src %in% complete.dists) %>%
  gather("key", "val", asia:africa) %>%
  group_by(key, priorName, src) %>%
  summarise(mean = mean(val))
```

##### Histograms

The vertical red line shows the mean of the distribution.

###### Uniform prior

```{r}
compute_map <- function(dist, prior.name, input.src, conjunct) {
  intermediate <- dist %>%
  filter(! src %in% complete.dists | src == "Prior") %>%
  gather("key", "val", asia:africa) %>%
  filter(key == conjunct, priorName == prior.name, src == input.src)
  map_estimate(intermediate$val)
}

# rs.l0.samp.map.inc <- tibble(
#   src = rep(c("Prior", "Elephants live in Africa.", 
#         "Elephants live in Africa and...", 
#         "Elephants live in Africa and Asia."), 6),
#   priorName = rep(rep(c("Uniform", "Multimodal", "U-shaped"), each=4), 2),
#   conjunct = rep(c("africa", "asia"), each=12)
# ) %>%
#   group_by(priorName, src, conjunct) %>%
#   summarise(map = compute_map(rs.l0.samp, priorName, src, conjunct))

rs.l0.samp.inc %>%
  filter(priorName == "Uniform") %>%
ggplot(aes(x = val))+
  geom_histogram(bins=21)+
  geom_vline(data=rs.l0.samp.mean.inc %>% filter(priorName == "Uniform"), aes(xintercept = mean), color = "red")+
  # geom_vline(data=rs.l0.samp.map.inc %>% filter(priorName == "Uniform"), aes(xintercept = map),col='blue')+
  facet_grid(key~src)
```


##### Violin plots

```{r}
ggplot(rs.l0.samp.inc,
       aes( x = key, y = val , fill = key))+
  geom_violin(adjust = 3.5, alpha = 0.3, color = 'black')+
  geom_point(data = rs.l0.samp.mean.inc,
         inherit.aes = T,
                 aes( x = key, y = mean, fill = key),
             position = position_dodge(width = 0.9),
             shape = 23, size = 3, stroke = 2)+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  facet_grid(priorName~src)+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.text.y = element_text(angle = 0),
        legend.position = "bottom")
```

#### Change in Prevalence Estimates

Here we show the change in prevalence estimates in the course of observing a full conjunctive generic "Elephants live in Africa and Asia", probing the model at four different points:
1. before the sentence (prior)
2. after the first predicate ("Elephants live in Africa")
3. after the "and" ("Elephants live in Africa and")
4. after the sentence ("Elephants live in Africa and Asia")

```{r}
rs.l0.change <- rs.l0.eleph %>%
         filter((src %in% c("prefix", "partial", "full")) | src == "prior") %>%
         select(both, me, everything()) %>%
  gather("conjunct", "prevalence", asia:africa) %>%
    mutate(
      weighted_prevalence = prob*prevalence, 
      src = factor(src, levels = c("prior", "prefix", "partial", "full"), labels = c("Prior", "Elephants live in Africa", "Elephants live in Africa and", "Elephants live in Africa and Asia"))) %>%
  group_by(src, priorName, conjunct) %>%
  summarize(expected_value = sum(weighted_prevalence))

ggplot(rs.l0.change,
       aes( x = src, y = expected_value, color = priorName))+
  geom_point()+
  geom_line(aes(group = priorName)) +
  facet_wrap(~conjunct)+
  ylab('Mean')+
  xlab('')
```


## Literal Listener - Effect of Strength of Mutual Exclusivity

The prior has a variable that specifies the strength of mutual exclusivity (the probability that the prior is correlated vs. uncorrelated). Here we investigate the effect of this variable.

```{r}
rs.l0.me <- data.frame()

for (meParam in meParams) {

  rs.eleph <- webppl(program_file = "elephants.wppl",
                   data = list(params = priorParameters[["uniform"]], multimodal = FALSE, meProb = meParam),
                   data_var = "priorInfo")

  rs.l0.me <- bind_rows(
    rs.l0.me,
    bind_rows(
      as.data.frame(rs.eleph$ambiguous_complete) %>%
        mutate(src = "ambiguous_complete"),
      as.data.frame(rs.eleph$cont1_complete) %>%
        mutate(src = "cont1_complete"),
      as.data.frame(rs.eleph$cont2_complete) %>%
        mutate(src = "cont2_complete"),
      as.data.frame(rs.eleph$prior) %>%
        mutate(src = "prior"),
      as.data.frame(rs.eleph$prefix) %>%
        mutate(src = "prefix"),
      as.data.frame(rs.eleph$full) %>%
        mutate(src = "full"),
      as.data.frame(rs.eleph$partial) %>%
        mutate(src = "partial")
    ) %>% rename(prob = probs,
               africa = support.africa,
               asia = support.asia,
               both = support.both,
               me = support.me) %>%
      mutate(priorName = priorName, meProb = meParam)
  )
}

rs.l0.samp.me <- get_samples(rs.l0.me, 50000) %>%
  mutate(
    priorName = factor(
      priorName,
      levels = c("uniform", "multimodal", "u_shaped", "multimodal2", "multimodal3", "bimodal"),
      labels = c("Uniform", "Multimodal", "U-shaped", "Multimodal v2", "multimodal3", "bimodal")
    ),
    src = factor(
      src,
      levels = c(
        "ambiguous_complete", "cont1_complete", "cont2_complete", "prior", "prefix", "partial", "full"
      ),
      labels = c(
        "Prior",
        "Ambiguous Complete",
        "And > Gen",
        "Gen > And",
        "Elephants live in Africa.",
        "Elephants live in Africa and...",
        "Elephants live in Africa and Asia."
      )
    )
  )
```

### Elephants live in Africa and Asia.

Again, we first consider the case of a complete utterance.

#### Joint distributions

```{r}
plot_joint_me <- function(dist, src.to.plot, cutoffs) {
  dist %>% 
    filter(src == src.to.plot) %>%
ggplot(., aes(x = africa, y = asia))+
  stat_density_2d(aes(fill = ..density..), 
                  geom = "raster", contour = FALSE) +
  scale_fill_viridis(option = "plasma")+
  xlab("% Africa")+
  ylab("% Asia")+
  facet_wrap(~meProb, labeller = labeller(facet_category = label_wrap_gen(width = 16)), nrow=2)+
  theme(strip.text.y = element_text(angle = 0),
        legend.position = 'bottom',
        panel.spacing.x=unit(3, "lines"),panel.spacing.y=unit(1, "lines"))+
  scale_x_continuous(limits = cutoffs, breaks = cutoffs)+
  scale_y_continuous(limits = cutoffs, breaks = cutoffs)+
  coord_fixed()
}
```

##### Prior

```{r}
plot_joint_me(rs.l0.samp.me, "Prior", c(0, 1))
```

##### Ambiguous

```{r}
plot_joint_me(rs.l0.samp.me, "Ambiguous Complete", c(0, 1))
```

##### And > Gen

```{r}
plot_joint_me(rs.l0.samp.me, "And > Gen", c(0, 1))
```

##### Gen > And

```{r}
plot_joint_me(rs.l0.samp.me, "Gen > And", c(0, 1))
```

#### Marginal Distributions

Red vertical lines show means of the distributions.

##### Histograms

###### Uniform prior

```{r}
estimate_mode <- function(x) {
  d = density(x)
  Estimate = d$x[which.max(d$x)]
  return(Estimate)
}
compute_map_me <- function(dist, input.src, conjunct, me) {
  intermediate <- dist %>%
  filter(src %in% complete.dists | src == "Prior") %>%
  gather("key", "val", asia:africa) %>%
  filter(key == conjunct, src == input.src, meProb == me)
  #intermediate
  estimate_mode(intermediate$val)
}

rs.l0.samp.mean.me <- rs.l0.samp.me %>%
  filter(src %in% complete.dists) %>%
  gather("key", "val", asia:africa) %>%
  group_by(key, priorName, src, meProb) %>%
  summarise(mean = mean(val))

# rs.l0.samp.map.me <- tibble(
#   src = rep(c("Prior", "Ambiguous Complete",
#         "Gen > And",
#         "And > Gen"), 10),
#   key = rep(c("africa", "asia"), each=20),
#   meProb = rep(1:10/10, 4)
# ) %>%
#   expand(src, key, meProb) %>%
#   group_by(src, key, meProb) %>%
#   summarise(map = compute_map_me(rs.l0.samp.me, src, key, meProb))

rs.l0.samp.me %>%
  filter(src %in% complete.dists) %>%
ggplot(aes(x = africa))+
  geom_histogram(bins=21)+
  geom_vline(data=rs.l0.samp.mean.me %>% filter(key == "africa"), aes(xintercept = mean), color = "red")+
  #geom_vline(data=rs.l0.samp.map.me %>% filter(key == "africa"), aes(xintercept = map), color='blue')+
  facet_grid(meProb~src)
```

##### Violin plots

###### Uniform prior

```{r}
ggplot(rs.l0.samp.me %>%
         filter(src %in% complete.dists) %>%
         gather(key, val, africa:asia),
       aes( x = key, y = val , fill = key))+
  geom_violin(adjust = 3.5, alpha = 0.3, color = 'black')+
  geom_point(data = rs.l0.samp.mean.me,
         inherit.aes = T,
                 aes( x = key, y = mean, fill = key),
             position = position_dodge(width = 0.9),
             shape = 23, size = 3, stroke = 2)+
  ylab("Implied prevalence rating")+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_fill_solarized()+
  scale_color_solarized()+
  facet_grid(meProb~src)+
  xlab("")+
  guides(fill = guide_legend(title = "Question"),
         color = guide_legend(title = "Question"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.text.y = element_text(angle = 0),
        legend.position = "bottom")
```

